### 2021-07-21 paper.tex
initial commit

\documentclass[10pt,a4paper]{article}

\usepackage{tgpagella}
\usepackage{graphicx}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{multicol}
\usepackage[ddmmyyyy]{datetime}
\usepackage[a4paper, margin=3cm]{geometry}

\begin{document}

	% Title page
	\begin{titlepage}
		\begin{center}

			\vspace*{1cm}

			% title
			\Huge
			\textbf{Brain Tumor Detection}

			\vspace{0.8cm}

			% logo
			\includegraphics[width=0.4\linewidth]{imgs/cu_logo.png}

			\vspace{1cm}

			\Large
			Department of Computer Science\\
			Gurudas College\\
			Calcutta University\\
			\today

			% subtitle
			\vspace{0.5cm}
			\textit{Detection of tumorous cells using machine learning models}

			\vspace{1cm}
			Submitted in partial fulfillment for the requirements for the
			degree of Bachelor of Science (Honors)

			\Large
			Academic Year: \textbf{2018-2021}

			\vfill
			% author
			\textbf{Authors}:

			$\bullet$ Shoptorshi \space\space
			$\bullet$ Brahmajit \space\space
			$\bullet$ Rajarshi \space\space
			$\bullet$ Bhargav

			% supervisor
			\vspace{0.5cm}
			\rule{5cm}{0.4pt}

			\textbf{Supervisor}: Kajari Bhattacharjeee

		\end{center}
	\end{titlepage}

	% certificate page
	\section*{\hfil \Huge Certificate\hfil}

	\begin{center}
		\vspace{1cm}

		% logo
		\includegraphics[width=0.3\linewidth]{imgs/cu_logo.png}

		\vspace{1cm}

		\Large
		Department of Computer Science\\
		Gurudas College\\
		Calcutta University\\
	\end{center}

	\vspace{1.8cm}
	This is to certify that the project entitled "Brain tumor detection using
	Machine Learning models" is a bona fide work of \textbf{Shoptorshi},
	\textbf{Brahmajit}, \textbf{Rajarshi} and \textbf{Bhargav} submitted to
	Gurudas College, University of Calcutta; in partial fulfillment of the
	requirement for the award of the degree "Bachelor of Science (Honors)" in
	Computer Science.
	\vfill

	\begin{multicols}{2}

		Supervisor:

		\rule{5cm}{0.4pt}

		\textbf{Kajari Bhattacharjeee}

		\vspace{1cm}

		Department Head:

		\rule{5cm}{0.4pt}

		\textbf{Srijeeta Charkraborty}

		\columnbreak

		Principal:

		\rule{5cm}{0.4pt}

		\textbf{Dr. Mausumi Chatterjee}

	\end{multicols}

\end{document}

### 2021-07-21 paper.tex
added table of content, and some other corrections

@@
-\documentclass[10pt,a4paper]{article}
+\documentclass[12pt]{article}
 
@@
 \usepackage[utf8]{inputenc}
+\usepackage[english]{babel}
 \usepackage{multicol}
@@
 \usepackage[a4paper, margin=3cm]{geometry}
+
+% sections on new page
+\usepackage{titlesec}
+\newcommand{\sectionbreak}{\clearpage}
+\setcounter{secnumdepth}{0}
+
+% index and clickable toc
+\usepackage{hyperref}
+\hypersetup{
+	colorlinks,
+	citecolor=black,
+	filecolor=black,
+	linkcolor=black,
+	urlcolor=black
+}
+
+% table of content name
+\addto\captionsenglish{% Replace "english" with the language you use
+	\renewcommand{\contentsname}%
+	{\hfill \Huge Table of Content \hfill}%
+}
 
@@
 
-			\vspace*{1cm}
+			\vspace*{0.5cm}
 
@@
 
-			\Large
+			\normalsize
 			Department of Computer Science\\
@@
 			\vspace{1cm}
+
+			\normalsize
 			Submitted in partial fulfillment for the requirements for the
-			degree of Bachelor of Science (Honors)
+			degree Bachelor of Science (Honors) in Computer Science.
 
-			\Large
 			Academic Year: \textbf{2018-2021}
@@
 			% supervisor
-			\vspace{0.5cm}
+			\vspace{1cm}
 			\rule{5cm}{0.4pt}
@@
 	% certificate page
-	\section*{\hfil \Huge Certificate\hfil}
+	\section[certificate]{\hfill \Huge Certificate \hfill}
+	\thispagestyle{empty}
+
+	\pagenumbering{roman}
 
@@
 
+	\section[acknowledgement]{\hfill \Huge Acknowledgement \hfill}
+	\label{sec:Acknowledgement}
+
+	I would like to express my special thanks of gratitude to our supervisor
+	\textbf{Kajari Bhattacharjeee}, teachers of our department \textbf{Sonali
+	Gupta} and department head \textbf{Srijeeta Charkraborty}; as well as our
+	principal ma'am \textbf{Dr. Mausumi Chatterjee} who gave us the golden
+	opportunity to do this wonderful project on \textit{Brain tumor detection},
+	which has also helped us in doing a lot of research and we came to know
+	about many new things.
+
+	We are really thankful to them.
+
+	Secondly we would like to thank the incredible authors of the research
+	papers in our references/citations for providing us with the information.
+
+	\tableofcontents
+
+	\section[abstract]{\hfill \Huge Abstract \hfill}
+
+	This is going to be fun.
 \end{document}

### 2021-07-21 paper.tex
first part of abstract added, needs more content

@@
 	\section[certificate]{\hfill \Huge Certificate \hfill}
-	\thispagestyle{empty}
+	%\thispagestyle{empty}
 
+	% roman page numbering
 	\pagenumbering{roman}
@@
 
-	\section[abstract]{\hfill \Huge Abstract \hfill}
+	% abstract
+	\section[abstract]{}
 
-	This is going to be fun.
+	% reverting back to normal page numbering
+	\pagenumbering{arabic}
+
+	\thispagestyle{plain}
+	\begin{center}
+		\Large
+		\textbf{Brain Tumor Detection}
+
+		\vspace{0.4cm}
+		\large
+		Using various machine learning models to detect brain tumor.
+
+		\vspace{0.4cm}
+		\textbf{Authors}:
+
+		$\bullet$ Shoptorshi \space\space
+		$\bullet$ Brahmajit \space\space
+		$\bullet$ Rajarshi \space\space
+		$\bullet$ Bhargav
+
+		\vspace{0.9cm}
+		\textbf{Abstract}
+	\end{center}
+
+	Tumors are cancerous or non-cancerous mass or growth of abnormal cells in
+	brain. Tumors can start in brain, or cancer elsewhere in the body can spread
+	to brain. There are many way to control the occurrence of these abnormal
+	cells. A tumor can be denoted as a malformed mass of tissues wherein the
+	cells multiply abruptly and ceaselessly, that is there is no control over
+	the growth of the cells.
+
+	The process of Image segmentation is adopted for extracting abnormal tumor
+	region within the brain. In the MRI (magnetic resonance image), segmentation
+	of brain tissue holds very significant in order to identify the presence of
+	outlines concerning the brain tumor. There is abundance of hidden
+	information in stored in the Health care sector. With appropriate use of
+	accurate data mining classification techniques, early prediction of any
+	disease can be effectively performed.
+
+	The project examines list of risk factors that are being traced out in brain
+	tumor surveillance systems. Also the method proposed assures to be highly
+	efficient and precise for brain tumor detection, classification and
+	segmentation. To achieve this precise automatic or semi-automatic methods
+	are needed. The project proposes an automatic segmentation method that
+	relies upon CNN (Convolution Neural Networks), VGG 16 and Resent 50,
+	determining small 7 x 7 kernels. By incorporating this single technique,
+	segmentation and classification is accomplished. CNN (a ML technique) from
+	NN (Neural Networks)wherein it has layer based for results classification.
+
 \end{document}

### 2021-07-21 paper.tex
abstract section complete

@@
 
-		\vspace{0.4cm}
-		\textbf{Authors}:
-
-		$\bullet$ Shoptorshi \space\space
-		$\bullet$ Brahmajit \space\space
-		$\bullet$ Rajarshi \space\space
-		$\bullet$ Bhargav
-
-		\vspace{0.9cm}
+		\vspace{0.5cm}
 		\textbf{Abstract}
@@
 	are needed. The project proposes an automatic segmentation method that
-	relies upon CNN (Convolution Neural Networks), VGG 16 and Resent 50,
-	determining small 7 x 7 kernels. By incorporating this single technique,
-	segmentation and classification is accomplished. CNN (a ML technique) from
-	NN (Neural Networks)wherein it has layer based for results classification.
+	relies upon \textit{ CNN (Convolution Neural Networks) }, \textit{ VGG 16 }
+	and \textit{ Resent 50 }, determining small 7 x 7 kernels. By incorporating
+	this single technique, segmentation and classification is accomplished. CNN
+	(a ML technique) from NN (Neural Networks)wherein it has layer based for
+	results classification.
+
+	Various levels involved in the proposed mechanisms are:
+
+	\begin{enumerate}
+		\item \textbf{ Data collection }
+		\item \textbf{ Pre-processing }
+		\item \textbf{ Average filtering }
+		\item \textbf{ segmentation }
+		\item \textbf{ feature extraction }
+		\item \textbf{CNN (or any other model) via classification and identification. By
+			utilizing the DM (data mining) techniques, significant relations and
+			patterns from the data can be extracted. The techniques of ML
+			(machine learning) and Data mining are being effectively employed
+			for brain tumor detection and prevention at an early stage.}
+	\end{enumerate}
+
+	\section[introduction]{\hfill \Huge Introduction \hfill}
+	\subsection[introduction]{\hfill \Huge Introduction \hfill}
 

### 2021-07-21 paper.tex
domain description and motivation

@@
-\documentclass[12pt]{article}
+\documentclass[11pt]{article}
 
-\usepackage{tgpagella}
+% font
+\usepackage{tgschola}
+
 \usepackage{graphicx}
@@
 	\section[introduction]{\hfill \Huge Introduction \hfill}
-	\subsection[introduction]{\hfill \Huge Introduction \hfill}
+	\subsection[domain description]{Domain Description}
+
+	\begin{enumerate}
+		\item \textbf{Neurological Examination}: It is a series of test to
+			measures the function of the patients nervous system and also
+			his/her physical and mental alertness.
+		\item \textbf{Machine Learning}: Machine learning approaches address
+			these problems by mainly using hand-crafted features (or pre-defined
+			features). As an initial step in this kind of segmentation, the key
+			information is extracted from the input image using some feature
+			extraction algorithm, and then a discriminative model is trained to
+			recognize the tumor from normal tissues. The designed machine
+			learning techniques generally employ hand-crafted features with
+			various classifiers, such as random forest, support vector machine
+			(SVM), fuzzy clustering. The designed methods and features
+			extraction algorithms have to extract features, edge-related
+			details, and other necessary information—which is time-consuming.
+			Moreover, when boundaries between healthy tissues and tumors are
+			fuzzy/vague, these methods demonstrate poorer performances.
+		\item \textbf{Brain Scan}: Brain scan is a picture of the internal
+			structure of the brain. A specialized machine takes a scan in the
+			same way as a digital camera takes a photograph. Using computer
+			technology, a scan compiles an image of the brain by photographing
+			it from various angles. Some types of scan uses contrast agent (or
+			contrast dye), which helps the doctor to see the difference between
+			normal and abnormal brain tissues.
+
+			MRI (Magnetic Resonance Imaging): It is a scanning device that uses
+			magnetic field and computer to capture images of the brain on films.
+			It does not use x-rays. It provides pictures from various planes,
+			which permits doctor to create a three-dimensional image of the
+			tumor. The MRI detects signals emitted from normal and abnormal
+			tissues, providing clear images of almost all tumors.
+	\end{enumerate}
+
+	\subsection[motivation]{Motivation}
+	The motivation is to develop a software with better segmentation capability
+	for use in medical imaging to detect diseases like brain tumor. Image
+	segmentation has been identified as the key problem of medical image
+	analysis and remains a popular and challenging area of research. Image
+	segmentation is increasingly used in many clinical and research applications
+	to analyze medical imaging datasets; which motivated us to present a
+	snapshot of dynamically changing field of medical image segmentation.
+
+	CT (Computed Tomography), MRI (Magnetic Resonance Imaging), PET (Positron
+	Emission Tomography) etc. generates a large amount of image information.
+	With the improved technology, not only does the size and resolution of the
+	images grow but also the number of dimensions increases. In the future, we
+	would like to have algorithms which can automatically detect diseases,
+	lesions and tumors, and highlight their locations in the large pile of
+	images.
+
+	The motivation of this work is to increase patient safety by providing
+	better and more precise data for medical decision.
 

### 2021-07-21 paper.tex
changed margin from 3cm to 2cm
made the acknowledgement page look a little better by added extra spaces

@@
 \usepackage[ddmmyyyy]{datetime}
-\usepackage[a4paper, margin=3cm]{geometry}
+\usepackage[a4paper, margin=2cm]{geometry}
 
@@
 
+	\vspace{1cm}
+
 	I would like to express my special thanks of gratitude to our supervisor
 	\textbf{Kajari Bhattacharjeee}, teachers of our department \textbf{Sonali
-	Gupta} and department head \textbf{Srijeeta Charkraborty}; as well as our
-	principal ma'am \textbf{Dr. Mausumi Chatterjee} who gave us the golden
-	opportunity to do this wonderful project on \textit{Brain tumor detection},
-	which has also helped us in doing a lot of research and we came to know
-	about many new things.
+	Gupta} and \textbf{Srijeeta Charkraborty} ( current department head ); as
+	well as our principal ma'am \textbf{Dr. Mausumi Chatterjee} who gave us the
+	golden opportunity to do this wonderful project on \textit{Brain tumor
+	detection}, which has also helped us in doing a lot of research and we came
+	to know about many new things.
 
 	We are really thankful to them.
+
+	\vspace{1cm}
 

### 2021-07-21 paper.tex
introduction complete

@@
 
+	\subsection[scope of work]{Scope of Work}
+	\subsubsection[deliverables]{Deliverables}
+	\begin{itemize}
+		\item Working program to take an MRI scan as input and predict presence
+			of tumorous cells with $\geq 90\%$ accuracy.
+	\end{itemize}
+
+	\subsubsection[scope]{Scope}
+	\begin{itemize}
+		\item The working program has external dependencies ( libraries ) and
+			it's expected to have a them installed for the program to work.
+	\end{itemize}
+
+	\subsubsection[timeline]{Timeline}
+	\begin{itemize}
+		\item \textbf{April 27, 2021} Project Assigned
+		\item \textbf{May 2, 2021} Project finalized by supervisor, and group is
+			divided into groups of two.
+		\item \textbf{May 3, 2021} Data collection started.
+		\item \textbf{May 12, 2021} Project Repository created and coding is
+			started.
+		\item \textbf{July 7, 2021} Coding is finished, documentation is
+			started.
+		\item \textbf{Just 21, 2021} Documentation complete.
+	\end{itemize}
+
+	\subsubsection[reports]{Reports}
+	\begin{itemize}
+		\item Constantly updating and pushing code to repository.
+		\item Both teams staying in touch with each other to keep up with each
+			others progress.
+		\item Report back to supervisor every once a week.
+	\end{itemize}
+
 \end{document}

### 2021-07-22 paper.tex
Added background and references. Bibliography has been added

@@
 }
+
+% bibliography
+\usepackage[
+	%backend=biber,
+	style=alphabetic,
+	citestyle=ieee
+]{biblatex}
+\usepackage{csquotes}
+
+\addbibresource{bibliography.bib}
 
@@
 
+	\section[background]{\hfill \Huge Background \hfill}
+
+	Natarajan \cite{bac1} proposed brain tumor detection method for MRI brain
+	images. The MRI brain images are first preprocessed using median filter,
+	then segmentation of image is done using threshold segmentation and
+	morphological operations are applied and then finally, the tumor region is
+	obtained using image subtraction technique. This approach gives the exact
+	shape of tumor in MRI brain image. Joshi \cite{bac2}  proposed brain tumor
+	detection and classification system in MR images by first extracting the
+	tumor portion from brain image, then extracting the texture features of the
+	detected tumor using Gray Level Co- occurrence Matrix (GLCM) and then
+	classified using neuro-fuzzy classifier. Amin and Mageed \cite{bac3}
+	proposed neural network and segmentation base system to automatically detect
+	the tumor in brain MRI images. The Principal Component Analysis (PCA) is
+	used for feature extraction and then Multi-Layer Perceptron (MLP) is used
+	classify the extracted features of MRI brain image.  The average recognition
+	rate is 88.2\% and peak recognition rate is 96.7\%.  Sapra \cite{bac4}
+	proposed image segmentation technique to detect brain tumor from MRI images
+	and then Probabilistic Neural Network (PNN)  is used for automated brain
+	tumor classification in MRI scans. PNN system proposed handle the process of
+	brain tumor classification more accurately. Suchita and Lalit \cite{bac5}
+	proposed unsupervised neural network learning technique for classification
+	of brain MRI images.  The MRI brain images are first preprocessed which
+	include noise filtering, edge detection, then the tumor is extracted using
+	segmentation. The texture features are extracted using Gray-Level
+	Co-occurrence Matrix(GLCM) and then Self-Organizing Maps (SOM) are used to
+	classify the brain as normal or abnormal brain, that is, whether it contain
+	tumor or not. Rajeshwari and Sharmila \cite{bac6} proposed preprocessing
+	techniques which are used to improve the quality of MRI image before using
+	it into an application. The average, median and wiener filters are used for
+	noise removal and interpolation based Discrete Wavelet Transform (DWT)
+	technique is used for resolution enhancement. The Peak Signal to Noise Ratio
+	(PSNR) is used for evaluation of these techniques.
+
+	\emergencystretch=1em
+	\printbibliography[title={\hfill \Huge References \hfill}]
+
 \end{document}

### 2021-07-23 paper.tex
biblatex style changed to numeric
certificate's department head signature
the "department head" was on a single line
leaving less space for signature, now they
are on different line.
Methodology added.
Need to put two images side by side for image acquisition section

@@
 \usepackage{tgschola}
+
+% sub figure
+\usepackage{caption}
+\usepackage{subcaption}
 
@@
 	%backend=biber,
-	style=alphabetic,
+	style=numeric,
 	citestyle=ieee
@@
 
-		Department Head:
+		Department
+
+		Head:
 
@@
 
+	\section[methodology]{\hfill \Huge Methodology \hfill}
+
+	As per literature survey, it was found that automated  brain  tumor
+	detection  is  very  necessary  as  high accuracy is needed when human life
+	is involved.  Automated detection of tumor in MR images involves feature
+	extraction and  classification  using  machine  learning  algorithm.  In
+	this paper, a system to automatically detect tumor in MR images is proposed
+	as shown in Figure~\ref{Proposed Methodology}
+
+	\begin{figure}[h]
+		\centering
+		\includegraphics[width=1\linewidth]{imgs/methodology}
+		\caption{Proposed Methodology}%
+		\label{Proposed Methodology}
+	\end{figure}
+
+	\textbf{ Image Acquisition: } The MRI brain images are acquired and are given as input
+	to pre-processing stage. The sample brain MR images are shown in figure 2.
+
+	%\textbf{ Preprocessing: } Preprocessing is needed as it provides improvement  in  image
+	%data  which    enhances  some  of  the  image  features  which  are
+	%important  for  further  processing.  The    pre-processing  steps  that
+	%are  applied  to  MR  image  are as follows :
+
 	\emergencystretch=1em
-	\printbibliography[title={\hfill \Huge References \hfill}]
+	\printbibliography[heading=bibintoc,title={References}]
 

### 2021-07-24 paper.tex
methodology done

@@
 \usepackage{tgschola}
-
-% sub figure
-\usepackage{caption}
-\usepackage{subcaption}
+\usepackage{amsmath}
 
 \usepackage{graphicx}
+\usepackage{subfig}
+\usepackage{float}
 \usepackage[T1]{fontenc}
@@
 
-	\textbf{ Image Acquisition: } The MRI brain images are acquired and are given as input
-	to pre-processing stage. The sample brain MR images are shown in figure 2.
+	\subsection{Image Acquisition}%
+	\label{sub:Image Acquisition}
 
-	%\textbf{ Preprocessing: } Preprocessing is needed as it provides improvement  in  image
-	%data  which    enhances  some  of  the  image  features  which  are
-	%important  for  further  processing.  The    pre-processing  steps  that
-	%are  applied  to  MR  image  are as follows :
+	The MRI brain images are acquired and are
+	given as input to pre-processing stage. The sample brain MR images are shown
+	in Figure~\ref{MRIScans}.
+
+	\begin{figure}[H]
+		\centering
+		\subfloat[MRI scan shown no presence of tumor]
+		{\includegraphics[width=0.4\linewidth]
+		{imgs/pred1.jpg}\label{scan2}}
+		\hspace{0.5cm}
+		\subfloat[MRI scan of a tumorous cell]
+		{\includegraphics[width=0.3\linewidth]
+		{imgs/Y100.JPG}\label{scan1}}
+		\caption{MRI Scans}
+		\label{MRIScans}
+	\end{figure}
+
+	\subsection{Preprocessing}%
+	\label{sub:Preprocessing}
+
+	Preprocessing is needed as it provides improvement
+	in image data which  enhances some of the image features which are important
+	for further processing. The  pre-processing steps that are applied to MR
+	image are as follows:
+
+	\begin{enumerate}
+		\item The  RGB  MR    image  is  converted  to  gray  scale image  and
+			then  median  filter  is  applied  for  noise  removal from brain MR
+			images as shown in Figure~\ref{smooted image}. The noise is to removed for further
+			processing as high accuracy is needed.
+
+		\item Then  edges  are  detected  from  filtered  image  using canny
+			edge  detection  as  shown  in  Figure~\ref{edge detection}.  The  edge detected
+			image is needed for segmentation of  the image
+
+		\item Then  watershed  segmentation  is  done  for  finding the
+			location  of  the  tumor  in  the  brain  image  as  shown  in
+			Figure~\ref{segmentation}. Segmentation is  the process of dividing  an image into
+			multiple segments. The aim of segmentation is to change
+			representation  of    image  into  something  which  is more  easy
+			to  analyze.  The result  of  watershed  segmentation is  label
+			image.    In  label  image,  all  the  different  objects identified
+			will  have  different  pixel  values  ,  all  the  pixels  of first
+			object  will have value 1, all the pixels of second object will have
+			value 2 and so on.
+	\end{enumerate}
+
+	\begin{figure}[H]
+		\centering
+		\subfloat[Original Image]
+		{\includegraphics[width=0.2\linewidth]
+		{imgs/Y100.JPG}\label{original}}
+		\hspace{0.5cm}
+		\subfloat[Filtered Imaage]
+		{\includegraphics[width=0.2\linewidth]
+		{imgs/median_filtering.png}\label{smooted image}}
+		\hspace{0.5cm}
+		\subfloat[Edge Detection]
+		{\includegraphics[width=0.2\linewidth]
+		{imgs/edges_detection.png}\label{edge detection}}
+		\hspace{0.5cm}
+		\subfloat[Segmentation]
+		{\includegraphics[width=0.2\linewidth]
+		{imgs/segmentation.png}\label{segmentation}}
+		\caption{preprocessing operations}
+		\label{Preprocessing Operations}
+	\end{figure}
+
+	\subsection{Feature Extraction}%
+	\label{sub:Feature Extraction}
+
+	When input to an algorithm is very large and
+	redundant to be processed, it is transformed into reduced representative set
+	of features called feature vector. Transformation of input data into set of
+	features is called feature extraction. In this step, the important features
+	needed for image classification are extracted. The segmented brain MR image
+	is used and texture features are extracted from the segmented image which
+	shows the texture property of the image. These features are extracted using
+	Gray Level Co-occurrence Matrix (GLCM) as it is robust method with high
+	performance.
+
+	The GLCM features are extracted as follows:
+
+	\begin{enumerate}
+		\item Energy: It gives a measure of textural uniformity, that is, measure
+			of pixel pair repetitions.
+
+			\begin{equation}
+				E = \sum^{N_g - 1}_{i=0} \sum^{N_g - 1}_{j=0} p(i, j)^2 \
+				\textnormal{ here, range = [0,1] }
+			\end{equation}
+
+		\item Contrast: It gives a measure of intensity contrast between a pixel
+			and its neighbor over the whole image.
+
+			\begin{equation}
+				Con = \sum^{N_g -1}_{n=0} n^2 \sum^{N_g -1}_{i=0} \sum^{N_g
+				-1}_{j=0} p(i,j)^2 \
+				\textnormal{ here, range = [0,1] }
+			\end{equation}
+
+		\item Correlation: It gives a measure of how correlated a pixel to its
+			neighbor over the whole image.
+
+			\begin{equation}
+				C = \frac{1}{\sigma^x \sigma^y}
+				\sum^{N_g - 1}_{i=0} \sum^{N_g -1}_{j=0} (i,j) p(i,j)^2
+				- \mu_x \mu_y \ \textnormal{here, range = [-1,1]}
+			\end{equation}
+
+		\item Homogeneity: It gives a measure of closeness of distribution of
+			elements in GLCM to GLCM diagonal.
+
+			\begin{equation}
+				H = \sum^{N_g -1}_{i=0} \sum^{N_g -1}_{j=0}
+				\frac{p(i,j)}{1 + \pmod{i,j}}
+				\ \textnormal{here, range = [0, 1]}
+			\end{equation}
+	\end{enumerate}
+
+	\subsection{Classification}%
+	\label{sub:Classification}
+
+	The Machine learning algorithms are used for
+	classification of MR brain image either as normal or abnormal.  The major
+	aim of ML algorithms is to automatically learn and make intelligent
+	decisions. The feature set formed by above specified method was applied to
+	Multi-Layer Perceptron (MLP) and Naive Bayes for classification.  MLP [3] is
+	a feed forward artificial neural network model that maps sets of input data
+	into a set of appropriate output. It is known as feed forward because it
+	does not contain any cycles and network output depends only on the current
+	input instance. In MLP, each node is a neuron with a nonlinear activation
+	function. It is based on supervised learning technique. Learning take place
+	by changing connection weights after each piece of data is processed, based
+	on the amount of error in the target output as compared to the expected
+	result. The goal of the learning procedure is to minimize error by improving
+	the current values of the weight associated with each edge. Because of this
+	backward changing process of the weights, model is named as
+	back-propagation.
+
+	Naive bayes is a supervised learning as well as statistical method for
+	classification. It is simple probabilistic classifier based on Bayes
+	theorem. It assumes that the value of a particular feature is unrelated to
+	the presence or absence of any other feature. The prior probability and
+	likelihood are calculated in order to calculate the posterior probability.
+	The method of maximum posterior probability is used for parameter
+	estimation. This method requires only a small amount of training data to
+	estimate the parameters which are needed for classification. The time taken
+	for training and classification is less.
 

### 2021-07-24 paper.tex
fixed space for ranges
convolutional layer added in methodology, user classification

@@
 \documentclass[11pt]{article}
+
+\usepackage[T1]{fontenc}
+\usepackage[utf8]{inputenc}
+\usepackage[english]{babel}
 
@@
 \usepackage{float}
-\usepackage[T1]{fontenc}
-\usepackage[utf8]{inputenc}
-\usepackage[english]{babel}
 \usepackage{multicol}
@@
 % bibliography
+\usepackage{url}
 \usepackage[
-	%backend=biber,
+	backend=biber,
 	style=numeric,
-	citestyle=ieee
+	%citestyle=ieee
 ]{biblatex}
@@
 				E = \sum^{N_g - 1}_{i=0} \sum^{N_g - 1}_{j=0} p(i, j)^2 \
-				\textnormal{ here, range = [0,1] }
+				\textnormal{ here, range = [0, 1] }
 			\end{equation}
@@
 				-1}_{j=0} p(i,j)^2 \
-				\textnormal{ here, range = [0,1] }
+				\textnormal{ here, range = [0, 1] }
 			\end{equation}
@@
 				\sum^{N_g - 1}_{i=0} \sum^{N_g -1}_{j=0} (i,j) p(i,j)^2
-				- \mu_x \mu_y \ \textnormal{here, range = [-1,1]}
+				- \mu_x \mu_y \ \textnormal{here, range = [-1, 1]}
 			\end{equation}
@@
 	decisions. The feature set formed by above specified method was applied to
-	Multi-Layer Perceptron (MLP) and Naive Bayes for classification.  MLP [3] is
+	Multi-Layer Perceptron (MLP) and Naive Bayes for classification.  MLP is
 	a feed forward artificial neural network model that maps sets of input data
@@
 
+	For classification three models are used; \textbf{CNN}, \textbf{VGG 16} and
+	\textbf{Resnet 50}.
+
+	\subsection{Convolutional Neural Network}%
+	\label{sub:Convolutional Neural Network}
+
+	CNN or Convolutional Neural Network a class of artificial neural network,
+	most commonly applied to analyze visual imagery.They are also known as
+	shift invariant or space invariant artificial neural networks (SIANN), based
+	on the shared-weight architecture of the convolution kernels or filters that
+	slide along input features and provide translation equivariant responses
+	known as feature maps. Counter-intuitively, most convolutional neural
+	networks are only equivariant, as opposed to invariant, to translation.
+	They have applications in image and video recognition, recommender
+	systems, image classification, image segmentation, medical image
+	analysis, natural language processing, brain-computer interfaces, and
+	financial time series.
+
+	\begin{figure}[h]
+		\centering
+		\includegraphics[width=0.8\linewidth]{imgs/cnn_arch.png}
+		\caption{CNN architecture}%
+		\label{CNN Architecture}
+	\end{figure}
+
+	\subsubsection{Architecture}
+
+	A convolutional neural network consists of an input layer, hidden layers and
+	an output layer. In any feed-forward neural network, any middle layers are
+	called hidden because their inputs and outputs are masked by the activation
+	function and final convolution. In a convolutional neural network, the
+	hidden layers include layers that perform convolutions. Typically this
+	includes a layer that performs a dot product of the convolution kernel with
+	the layer's input matrix.  This product is usually the Frobenius inner
+	product, and its activation function is commonly ReLU. As the convolution
+	kernel slides along the input matrix for the layer, the convolution
+	operation generates a feature map, which in turn contributes to the input of
+	the next layer. This is followed by other layers such as pooling layers,
+	fully connected layers, and normalization layers \cite{covnet_arch}.
+
+	\textbf{Convolutional Layer}:
+	In a CNN, the input is a tensor with a shape: (number of inputs) x (input
+	height) x (input width) x (input channels). After passing through a
+	convolutional layer, the image becomes abstracted to a feature map, also
+	called an activation map, with shape: (number of inputs) x (feature map
+	height) x (feature map width) x (feature map channels). A convolutional
+	layer within a CNN generally has the following attributes:
+
+	\begin{itemize}
+		\item Convolutional filters/kernels defined by a width and height (hyper-parameters).
+		\item The number of input channels and output channels
+			(hyper-parameters). One layer's input channels must equal the number
+			of output channels (also called depth) of its input.
+		\item Additional hyperparameters of the convolution operation, such as:
+			padding, stride, and dilation.
+	\end{itemize}
+
+	Convolutional layers convolve the input and pass its result to the next
+	layer. This is similar to the response of a neuron in the visual cortex to a
+	specific stimulus.
+
+	\textbf{Pooling Layer}:
+	Convolutional networks may include local and/or global pooling layers along
+	with traditional convolutional layers. Pooling layers reduce the dimensions
+	of data by combining the outputs of neuron clusters at one layer into a
+	single neuron in the next layer. Local pooling combines small clusters,
+	tiling sizes such as 2 x 2 are commonly used. Global pooling acts on all the
+	neurons of the feature map. There are two common types of pooling in popular
+	use: max and average. Max pooling uses the maximum value of each local
+	cluster of neurons in the feature map, while average pooling takes the
+	average value.
+
+	\textbf{ReLU Layer}:
+
+	ReLU is the abbreviation of rectified linear unit, which applies the
+	non-saturating activation function
+	\begin{equation}
+		f ( x ) = \max ( 0 , x )
+	\end{equation}
+
+	.It effectively removes
+	negative values from an activation map by setting them to zero. It
+	introduces nonlinearities to the decision function and in the overall
+	network without affecting the receptive fields of the convolution layers.
+
+	Other functions can also be used to increase nonlinearity, for example the
+	saturating hyperbolic tangent
+	\begin{equation}
+	f(x)=\tanh(x)
+	f(x) = | \tanh (x) |
+	\end{equation}
+	and the
+	sigmoid function
+
+	\begin{equation}
+		\sigma(x) = (1+e^{-x})^{-1}
+	\end{equation}
+
+	ReLU is often preferred to other functions because it trains the neural network several
+	times faster without a significant penalty to generalization accuracy
+	 \cite{relu_layer}.
+
+	\textbf{Fully Connected Layer}
+
+	After several convolutional and max pooling layers, the final classification
+	is done via fully connected layers. Neurons in a fully connected layer have
+	connections to all activations in the previous layer, as seen in regular
+	(non-convolutional) artificial neural networks. Their activations can thus
+	be computed as an affine transformation, with matrix multiplication followed
+	by a bias offset (vector addition of a learned or fixed bias term).
+
+	\textbf{Loss Layer}
+
+	The "loss layer", or "loss function", specifies how training penalizes the
+	deviation between the predicted output of the network, and the true data
+	labels (during supervised learning). Various loss functions can be used,
+	depending on the specific task.
+
+	The Softmax loss function is used for predicting a single class of K
+	mutually exclusive classes. Sigmoid cross-entropy loss is used for
+	predicting K independent probability values is $[0, 1]$.  Euclidean loss is
+	used for regressing to real-valued labels $(- \infty, \infty)$.
+
+	\textbf{Receptive field}
+
+	In neural networks, each neuron receives input from some number of locations
+	in the previous layer. In a convolutional layer, each neuron receives input
+	from only a restricted area of the previous layer called the neuron's
+	receptive field. Typically the area is a square (e.g. 5 by 5 neurons).
+	Whereas, in a fully connected layer, the receptive field is the entire
+	previous layer. Thus, in each convolutional layer, each neuron takes input
+	from a larger area in the input than previous layers. This is due to
+	applying the convolution over and over, which takes into account the value
+	of a pixel, as well as its surrounding pixels. When using dilated layers,
+	the number of pixels in the receptive field remains constant, but the field
+	is more sparsely populated as its dimensions grow when combining the effect
+	of several layers.
+
+	\textbf{Weights}
+
+	Each neuron in a neural network computes an output value by applying a
+	specific function to the input values received from the receptive field in
+	the previous layer. The function that is applied to the input values is
+	determined by a vector of weights and a bias (typically real numbers).
+	Learning consists of iteratively adjusting these biases and weights.
+
+	The vector of weights and the bias are called filters and represent
+	particular features of the input (e.g., a particular shape). A
+	distinguishing feature of CNNs is that many neurons can share the same
+	filter. This reduces the memory footprint because a single bias and a single
+	vector of weights are used across all receptive fields that share that
+	filter, as opposed to each receptive field having its own bias and vector
+	weighting.
+
+	%\subsection{VGG 16}
+
+	\section[implementation]{\hfill \Huge Implementation \hfill}
+
+	\subsection{Assumptions and Dependencies}%
+	\label{sub:Assumptions and Dependencies}
+	It is assumed that the MRI scans are collected and processed before feeding
+	into the module.
+
+	The program is dependent on external modules and are expected to be
+	pre-installed on the system. The modules namely include:
+
+	\begin{itemize}
+		\item \href{https://www.fast.ai/}{fast.ai}
+		\item \href{https://www.tensorflow.org/}{tensorflow}
+		\item \href{https://opencv.org/}{OpenCV}
+		\item \href{https://matplotlib.org/}{matplotlib}
+	\end{itemize}
+
+	\subsection{Implementation Methods}%
+	\label{sub:Implementation Methods}
+	After acquiring the data, the data is classified into two classes (binary
+	class) of yes, consisting of tumorous cell and no, not consisting tumorous
+	cells. A second batch of images is kept separate for prediction, the
+	prediction batch.
+
+	Next three machine learning models are created. A \textbf{CNN} or a
+	convolutional neural network, \textbf{VGG 16} and \textbf{Resnet 50}.
+
 	\emergencystretch=1em

### 2021-07-24 paper.tex
numbered sections and section names are not in center

@@
 \newcommand{\sectionbreak}{\clearpage}
-\setcounter{secnumdepth}{0}
+%\setcounter{secnumdepth}{0}
 
@@
 	% certificate page
-	\section[certificate]{\hfill \Huge Certificate \hfill}
+	\section*{\hfill \Huge Certificate \hfill}
 	%\thispagestyle{empty}
@@
 
-	\section[acknowledgement]{\hfill \Huge Acknowledgement \hfill}
+	\section*{Acknowledgement}
 	\label{sec:Acknowledgement}
@@
 	% abstract
-	\section[abstract]{}
+	\section[abstract]{Abstract}
 
@@
 		Using various machine learning models to detect brain tumor.
-
-		\vspace{0.5cm}
-		\textbf{Abstract}
 	\end{center}
@@
 
-	\section[introduction]{\hfill \Huge Introduction \hfill}
+	\section[introduction]{Introduction}
 	\subsection[domain description]{Domain Description}
@@
 
-	\section[background]{\hfill \Huge Background \hfill}
+	\section[background]{Background}
 
@@
 
-	\section[methodology]{\hfill \Huge Methodology \hfill}
+	\section[methodology]{Methodology}
 
@@
 
-	%\subsection{VGG 16}
+	\subsection{VGG 16}
 
-	\section[implementation]{\hfill \Huge Implementation \hfill}
+	VGG 16 is is a significantly more accurate ConvNet architecture, which not
+	only achieve state-of-the-art accuracy on ILSVRC classification and
+	localisation tasks, but are also applicable to other image recognition
+	datasets, where they achieve excellent performance even when used as a part
+	of a relatively simple pipelines (e.g. deep features classified by a linear
+	SVM without fine-tuning).
+
+	\subsubsection{Architecture}
+	\label{sssec:vgg arch}
+
+	During training, the input to our ConvNets is a fixed-size 224 × 224 RGB
+	image. The only pre- processing we do is subtracting the mean RGB value,
+	computed on the training set, from each pixel.  The image is passed through
+	a stack of convolutional (conv.) layers, where we use filters with a very
+	small receptive field: 3 × 3 (which is the smallest size to capture the
+	notion of left/right, up/down, center). In one of the configurations we also
+	utilise 1 × 1 convolution filters, which can be seen as a linear
+	transformation of the input channels (followed by non-linearity). The
+	convolution stride is fixed to 1 pixel; the spatial padding of conv. layer
+	input is such that the spatial resolution is preserved after convolution,
+	i.e. the padding is 1 pixel for 3 × 3 conv. layers. Spatial pooling is
+	carried out by five max-pooling layers, which follow some of the conv.
+	layers (not all the conv. layers are followed by max-pooling). Max-pooling
+	is performed over a 2 × 2 pixel window, with stride 2.
+
+	\begin{figure}[h]
+		\centering
+		\includegraphics[width=0.5\linewidth]{imgs/vgg16_arch.png}
+		\caption{VGG Architecture}%
+		\label{fig:vgg_arch}
+	\end{figure}
+
+	A stack of convolutional layers (which has a different depth in different
+	architectures) is followed by three Fully-Connected (FC) layers: the first
+	two have 4096 channels each, the third performs 1000- way ILSVRC
+	classification and thus contains 1000 channels (one for each class). The
+	final layer is the soft-max layer. The configuration of the fully connected
+	layers is the same in all networks.
+
+	All hidden layers are equipped with the rectification (ReLU) non-linearity.
+	We note that none of our networks (except for one) contain Local Response
+	Normalisation (LRN) normalisation: as will be shown in Sect. 4, such
+	normalisation does not improve the performance on the ILSVRC dataset, but
+	leads to increased memory con- sumption and computation time. Where
+	applicable, the parameters for the LRN layer are those of.
+
+	\subsubsection{Configuration}
+
+	The ConvNet configurations, evaluated in this paper, are outlined in Table
+	1, one per column. In the following we will refer to the nets by their names
+	(A–E).  All configurations follow the generic design presented in
+	Section~\ref{sssec:vgg arch} and differ only in the depth: from 11 weight
+	layers in the network A (8 conv. and 3 FC layers) to 19 weight layers in the
+	network E (16 conv. and 3 FC layers). The width of conv. layers (the number
+	of channels) is rather small, starting from 64 in the first layer and then
+	increasing by a factor of 2 after each max-pooling layer, until it reaches
+	512.
+
+	\begin{figure}[h]
+		\centering
+		\includegraphics[width=0.8\linewidth]{imgs/vgg16_conf}
+		\caption{VGG16 configuration}%
+		\label{fig:vgg16_conf}
+	\end{figure}
+
+	\section[implementation]{Implementation}
 

### 2021-07-24 paper.tex
All architectures added.
Methodology is complete. Implementation needs to be done.

@@
 \usepackage[english]{babel}
+\usepackage{microtype}
 
@@
 \addbibresource{bibliography.bib}
+
+\usepackage{wrapfig}
 
@@
 	of a relatively simple pipelines (e.g. deep features classified by a linear
-	SVM without fine-tuning).
+	SVM without fine-tuning) \cite[1]{simonyan2015deep}.
 
@@
 	\label{sssec:vgg arch}
+
+	\begin{wrapfigure}{r}{0.5\textwidth}
+		\begin{center}
+			\includegraphics[ width=0.5\textwidth ]{imgs/vgg16_arch.png}
+		\end{center}
+		\caption{VGG Architecture}
+	\end{wrapfigure}
 
@@
 
-	\begin{figure}[h]
-		\centering
-		\includegraphics[width=0.5\linewidth]{imgs/vgg16_arch.png}
-		\caption{VGG Architecture}%
-		\label{fig:vgg_arch}
-	\end{figure}
-
 	A stack of convolutional layers (which has a different depth in different
@@
 	normalisation does not improve the performance on the ILSVRC dataset, but
-	leads to increased memory con- sumption and computation time. Where
-	applicable, the parameters for the LRN layer are those of.
+	leads to increased memory con- sumption and computation time.
+	\cite[1]{simonyan2015deep}
 
@@
 
-	The ConvNet configurations, evaluated in this paper, are outlined in Table
-	1, one per column. In the following we will refer to the nets by their names
-	(A–E).  All configurations follow the generic design presented in
-	Section~\ref{sssec:vgg arch} and differ only in the depth: from 11 weight
-	layers in the network A (8 conv. and 3 FC layers) to 19 weight layers in the
-	network E (16 conv. and 3 FC layers). The width of conv. layers (the number
-	of channels) is rather small, starting from 64 in the first layer and then
-	increasing by a factor of 2 after each max-pooling layer, until it reaches
-	512.
+	The ConvNet configurations, evaluated in this paper, are outlined in
+	Figure~\ref{fig:vgg16_conf}, one per column. In the following we will refer
+	to the nets by their names (A–E).  All configurations follow the generic
+	design presented in Section~\ref{sssec:vgg arch} and differ only in the
+	depth: from 11 weight layers in the network A (8 conv. and 3 FC layers) to
+	19 weight layers in the network E (16 conv. and 3 FC layers). The width of
+	conv. layers (the number of channels) is rather small, starting from 64 in
+	the first layer and then increasing by a factor of 2 after each max-pooling
+	layer, until it reaches 512.
+	\cite[3]{simonyan2015deep}
 
@@
 		\centering
-		\includegraphics[width=0.8\linewidth]{imgs/vgg16_conf}
+		\includegraphics[width=\linewidth]{imgs/vgg16_conf}
 		\caption{VGG16 configuration}%
 		\label{fig:vgg16_conf}
+	\end{figure}
+
+	\subsection{ResNet 50}%
+	\label{sub:ResNet 50}
+
+	\subsubsection{Residual Learning}
+
+	\begin{wrapfigure}{r}{0.5\textwidth}
+		\begin{center}
+			\includegraphics[ width=0.5\textwidth ]{imgs/resnet_arch2.png}
+		\end{center}
+		\caption{Resnet Architecture}
+	\end{wrapfigure}
+
+	Let us consider $H(x)$ as an underlying mapping to be fit by a few stacked
+	layers (not necessarily the entire net), with $x$ denoting the inputs to the
+	first of these layers. If one hypothesizes that multiple nonlinear layers
+	can asymptotically approximate complicated functions, then it is equivalent
+	to hypothesize that they can asymptotically approximate the residual
+	functions, i.e., $H(x) - x$ (assuming that the input and output are of the
+	same dimensions). So rather than expect stacked layers to approximate $H(x)$
+	, we explicitly let these layers approximate a residual function
+	\begin{equation}
+		F(x) = H(x) - x
+	\end{equation}
+	The original function thus becomes $F(x) + x$. Although both forms should be
+	able to asymptot- ically approximate the desired functions (as
+	hypothesized), the ease of learning might be different \cite[3]{he2015deep}.
+
+	\subsubsection{Network Architecture}
+
+	The plain/residual network was tested as follows:
+
+	\textbf{Plain Network}
+
+	Our plain baselines are mainly inspired by the philosophy of VGG nets.  The
+	convolutional layers mostly have 3×3 filters and follow two simple design
+	rules:
+
+	\begin{enumerate}
+		\item for the same output feature map size, the layers have the same
+			number of filters
+		\item if the feature map size is halved, the number of filters is
+			doubled so as to preserve the time complexity per layer.
+	\end{enumerate}
+
+	We perform downsampling directly by convolutional layers that have a stride
+	of 2. The network ends with a global average pooling layer and a 1000-way
+	fully-connected layer with softmax. The total number of weighted layers are
+	34.  It is worth noticing that our model has fewer filters and lower
+	complexity than VGG nets. Our 34-layer baseline has 3.6 billion FLOPs
+	(multiply-adds), which is only 18\% of VGG-19 (19.6 billion FLOPs)
+	\cite[3]{he2015deep} .
+
+	\textbf{Residual Network}
+	Based on the above plain network, we insert shortcut connections which turn
+	the network into its counterpart residual version. The identity shortcuts
+	can be directly used when the input and output are of the same dimensions.
+	When the dimensions increase, we consider two options:
+	\begin{enumerate}
+		\item The shortcut still performs identity mapping, with extra zero
+			entries padded for increasing dimensions. This option introduces no
+			extra parameter
+		\item The projection shortcut is used to match dimensions (done by 1×1
+			convolutions).
+	\end{enumerate}
+	For both options, when the shortcuts go across feature maps of two sizes,
+	they are performed with a stride of 2 \cite[4]{he2015deep} .
+
+	\begin{figure}[h]
+		\centering
+		\includegraphics[width=\linewidth]{imgs/resnet_arch.png}
+		\caption{resnet50 configuration}%
+		\label{fig:resnet conf}
 	\end{figure}

### 2021-07-24 paper.tex
result done, almost complete

@@
 	Next three machine learning models are created. A \textbf{CNN} or a
-	convolutional neural network, \textbf{VGG 16} and \textbf{Resnet 50}.
+	convolutional neural network, \textbf{VGG 16} and \textbf{Resnet 50}. The
+	models are implemented in both fast.ai and tensorflow, to be compared later.
+
+	While training the images are resized to $(150 \times 150)$ and augmented at
+	runtime, thus removing bias as much as possible. Since there are only two
+	possible classes (yes and no), a binary class is sufficient; dividing the
+	images into training and testing (validation set) in $80:20$ ratio. Giving
+	us $2603 \ \textnormal{and} \ 650$ images for the \textit{yes} and
+	\textit{no} classes, respectively.
+
+	After training is complete the models are then evaluated (further discussed
+	in Section~\ref{sec:result} )
+
+	\section{Result}%
+	\label{sec:result}
+
+	The evaluated models are plotted on graph for better understanding of data.
+
+	\begin{figure}[H]
+		\centering
+		\subfloat[vgg16 using tensorflow]
+		{\includegraphics[width=0.4\linewidth]
+		{imgs/tf_vgg16.png}\label{tf_vgg16}}
+		\hspace{0.5cm}
+		\subfloat[vgg16 using fast.ai]
+		{\includegraphics[width=0.5\linewidth]
+		{imgs/fastai_vgg16.png}\label{fastai_vgg16}}
+		\caption{VGG16 implemented in fast.ai and tensorflow}
+		\label{VGG16 in fast.ai and tensorflow}
+	\end{figure}
+
+	\begin{figure}[H]
+		\centering
+		\subfloat[resnet50 using tensorflow]
+		{\includegraphics[width=0.4\linewidth]
+		{imgs/tf_resnet.png}\label{tf_resnet}}
+		\hspace{0.5cm}
+		\subfloat[resnet50 using fast.ai]
+		{\includegraphics[width=0.5\linewidth]
+		{imgs/fastai_resnet.png}\label{fastai_resnet}}
+		\caption{Resnet 50 implemented in fast.ai and tensorflow}
+		\label{ResNet 50 in fast.ai and tensorflow}
+	\end{figure}
+
+	We have achieved around 96\% and 98\% accuracy for for the VGG16 and ResNet,
+	respectively; using \textit{tensorflow}, and 97\% (98\% after unfreezing)
+	and 97\% (99\% after unfreezing) using \textit{fast.ai}. While using CNN
+	accuracy was almost same when implemented by the both the libraries.
+
+	There are lot of room for improvement but due to time and hardware
+	constrains we were able to only implement till such.
+
+	\begin{figure}[ht]
+		\centering
+		\includegraphics[width=\linewidth]{imgs/result.png}
+		\caption{Predictions made by the VGG16 model in tensorflow on random data}%
+		\label{fig:result}
+	\end{figure}
+
+	As it can be seen from Figure~\ref{fig:result} there are some false
+	positives in our predictions.
 

### 2021-07-25 tf_prediction.tex
code implementation using tensorflow

\begin{minted}{python}
import tensorflow as tf
from keras_preprocessing.image import img_to_array
from tensorflow.keras.preprocessing.image import ImageDataGenerator
from tensorflow.keras.applications.resnet50 import preprocess_input, decode_predictions
from tensorflow.keras.preprocessing import image
from tensorflow.keras.preprocessing import image_dataset_from_directory
import matplotlib.image as mpimg
from keras.preprocessing import image
import cv2
import os
import glob

import numpy as np
import matplotlib.pyplot as plt

model = tf.keras.models.load_model('/content/gdrive/MyDrive/model/vgg_imp.h5')

training_dataset_directory = '/content/dataset/training'
testing_dataset_directory = '/content/dataset/testing'

train_datagen = ImageDataGenerator(
    rotation_range=20,
    width_shift_range=0.2,
    height_shift_range=0.2,
    horizontal_flip=True,
    vertical_flip=True,
    preprocessing_function=preprocess_input,
    validation_split=0.2
)

img_size = (150, 150)
img_shape = img_size + (3,)
random_seed = 123

training_set = train_datagen.flow_from_directory(
    training_dataset_directory,
    target_size=img_size,
    class_mode='binary',
    subset='training'
)

testing_set = train_datagen.flow_from_directory(
    testing_dataset_directory,
    target_size=img_size,
    class_mode='binary',
    subset='validation'
)

loss, acc = model.evaluate(training_set)

IMG_SIZE = (150,150)
BATCH_SIZE = 32
new_dataset = image_dataset_from_directory(
    '/content/gdrive/MyDrive/dataset',
    image_size=IMG_SIZE
)

predictions = model.predict(new_dataset,batch_size=BATCH_SIZE)

img_dir = "/content/gdrive/MyDrive/dataset/pred"
data_path = os.path.join(img_dir,'*g')
files = glob.glob(data_path)
data = []
result = []
for f1 in files:
    test_image = image.load_img(f1, target_size = (150, 150))
    test_image = image.img_to_array(test_image)
    test_image = np.expand_dims(test_image, axis = 0)
    images = np.vstack([test_image])
    classes = model.predict(images, batch_size=10)
    classes = np.round(classes)
    data.append(f1)
    result.append(classes)

for x,y in zip(data, result):
  print(x, y)

img = cv2.imread(data[0])
plt.imshow(img)
plt.title(result[0])

L = 4
W = 4
fig, axes = plt.subplots(L, W, figsize = (12,12))
axes = axes.ravel()
for i in np.arange(0, L * W):
    img = cv2.imread(data[i])
    axes[i].imshow(img)
    axes[i].set_title(result[i])
    axes[i].set_xticks([])
    axes[i].set_yticks([])
\end{minted}

### 2021-07-25 tf_reset.tex
code implementation using tensorflow

\begin{minted}{python}
from tensorflow.keras.preprocessing.image import ImageDataGenerator
from tensorflow.keras.applications.resnet50 import ResNet50, preprocess_input
from tensorflow.keras.models import Sequential
from tensorflow.keras.layers import Flatten, Dropout, Dense
from tensorflow.keras.optimizers import RMSprop, Adam, SGD
from matplotlib import pyplot as plt

training_dataset_directory = '/content/dataset/training'
testing_dataset_directory = '/content/dataset/testing'

train_datagen = ImageDataGenerator(
    rotation_range=20,
    width_shift_range=0.2,
    height_shift_range=0.2,
    horizontal_flip=True,
    vertical_flip=True,
    preprocessing_function=preprocess_input,
    validation_split=0.2
)

img_size = (150, 150)
img_shape = img_size + (3,)
random_seed = 123

training_set = train_datagen.flow_from_directory(
    training_dataset_directory,
    target_size=img_size,
    batch_size=32,
    class_mode='binary',
    subset='training'
)

testing_set = train_datagen.flow_from_directory(
    testing_dataset_directory,
    target_size=img_size,
    class_mode='binary',
    subset='validation'
)

img_size = (150, 150)
img_shape = img_size + (3,)
random_seed = 123

resnet50 = ResNet50(
    weights='imagenet',
    include_top=False,
    input_shape=img_shape
)

num_classes = 1
model = Sequential()
model.add(resnet50)
model.add(Flatten())
model.add(Dense(256, activation='relu'))
model.add(Dropout(0.5))
model.add(Dense(num_classes, activation='sigmoid'))
model.layers[0].trainable = False
model.summary()

model.compile(
    loss='binary_crossentropy',
    optimizer='Adam',
    metrics=['accuracy']
)

epochs = 30
history = model.fit(
    training_set,
    epochs=epochs,
    validation_data=testing_set,
)
\end{minted}

### 2021-07-25 tf_vgg.tex
code implementation using tensorflow

--- 2021-07-25 tf_reset.tex
@@
 \begin{minted}{python}
+import tensorflow as tf
 from tensorflow.keras.preprocessing.image import ImageDataGenerator
-from tensorflow.keras.applications.resnet50 import ResNet50, preprocess_input
+from tensorflow.keras.applications.vgg16 import VGG16, preprocess_input
 from tensorflow.keras.models import Sequential
 from tensorflow.keras.layers import Flatten, Dropout, Dense
-from tensorflow.keras.optimizers import RMSprop, Adam, SGD
 from matplotlib import pyplot as plt
@@
     target_size=img_size,
-    batch_size=32,
     class_mode='binary',
@@
 
-resnet50 = ResNet50(
+vgg16 = VGG16(
     weights='imagenet',
@@
 model = Sequential()
-model.add(resnet50)
+model.add(vgg16)
 model.add(Flatten())

### 2021-07-25 fastai_resnet.tex
resnet and vgg using fastai

\begin{minted}{python}
import numpy as np
import pandas as pd
import torch
import keras
import os
import gc
import pathlib
from sklearn.metrics import confusion_matrix
from fastai import *
from fastai.vision.all import *
from fastai.tabular.all import *
from fastai.text.all import *
from fastai.vision.data import ImageDataLoaders
from fastai.vision.models import *
import torchvision.models as models
from fastai.callback.schedule import lr_find
from fastai.callback.schedule import *
from matplotlib import pyplot as plt
from fastai.imports import *
from fastai.torch_core import *
from fastai.learner import *

print(os.listdir("/content/drive/MyDrive/Colab Notebooks/samples"))
DATA_DIR = "/content/drive/MyDrive/Colab Notebooks/samples/Brain_Tumor"
os.listdir(f'{DATA_DIR}')

data = ImageDataLoaders.from_folder(
    DATA_DIR,
    train=".",
    valid_pct=0.2,
    ds_tfms=aug_transforms(
        mult=1.0,
        do_flip=True,
        flip_vert=True,
        max_warp=0,
        max_rotate=10.0,
        max_zoom=1.1,
        max_lighting=0.2,
        p_affine=0.75,
        mode='bilinear',
        pad_mode='reflection',
        align_corners=True,
        min_scale=1.0),
    item_tfms=Resize(224),
    bs=64,
    val_bs=None,
    num_workers=0,
    batch_tfms=Normalize.from_stats(
        *imagenet_stats))

data.show_batch(nrows=4, figsize=(10, 10))

learner = cnn_learner(
    data, models.resnet50, metrics=[
        accuracy, error_rate], cbs=[
            ShowGraphCallback()], model_dir="/tmp/model/")

learner.lr_find()

learner.model

learner.fit_one_cycle(6, lr_max=slice(8.32e-4), cbs=[ShowGraphCallback()])

learner.export(
    "/content/drive/MyDrive/Colab Notebooks/pretrained_model/resnet/btc2.pkl")

learner.unfreeze()

learner.lr_find()

learner.fit_one_cycle(
    6,
    lr_max=slice(5.754399353463668e-6),
    cbs=[
        ShowGraphCallback()])

learner.fit_one_cycle(4, lr_max=slice(2.7e-5), cbs=[ShowGraphCallback()])

learner.fit_one_cycle(4, lr_max=slice(2.9e-5), cbs=[ShowGraphCallback()])

learner.export(
    "/content/drive/MyDrive/Colab Notebooks/pretrained_model/resnet/final_resnet/btc_final2.pkl")

interp = ClassificationInterpretation.from_learner(learner)

interp.plot_top_losses(25, figsize=(20, 20))

interp.plot_confusion_matrix(figsize=(8, 8), dpi=60)
\end{minted}

### 2021-07-25 paper.tex
results in toc was Result instead of result, changed that
appendix added, code implementation using tensorflow done
fast.ai implementation added
Background separted, added cnn result and code
Background is now in separte file

Code for CNN has been added and predictions for fast.ai

two differnent prediction images

cnn's comparsion graph added too.

@@
 
+% fonts
 \usepackage[T1]{fontenc}
@@
 \usepackage{microtype}
-
-% font
 \usepackage{tgschola}
+\usepackage{inconsolata}
 \usepackage{amsmath}
 
+% images
 \usepackage{graphicx}
@@
 \usepackage[a4paper, margin=2cm]{geometry}
+\usepackage{wrapfig}
+
+% code listing
+\usepackage{minted}
+\usemintedstyle{tango}
 
@@
 % bibliography
+\usepackage{bookmark}
 \usepackage{url}
@@
 
-\usepackage{wrapfig}
-
 % table of content name
-\addto\captionsenglish{% Replace "english" with the language you use
-	\renewcommand{\contentsname}%
-	{\hfill \Huge Table of Content \hfill}%
-}
+%\usepackage[nottoc]{tocbibind}
+%\renewcommand{\theHsection}{\thepart.section.\thesection}
+%\addto\captionsenglish{% Replace "english" with the language you use
+	%\renewcommand{\contentsname}%
+	%{\hfill \Huge Table of Content \hfill}%
+%}
 
@@
 	\section[background]{Background}
-
-	Natarajan \cite{bac1} proposed brain tumor detection method for MRI brain
-	images. The MRI brain images are first preprocessed using median filter,
-	then segmentation of image is done using threshold segmentation and
-	morphological operations are applied and then finally, the tumor region is
-	obtained using image subtraction technique. This approach gives the exact
-	shape of tumor in MRI brain image. Joshi \cite{bac2}  proposed brain tumor
-	detection and classification system in MR images by first extracting the
-	tumor portion from brain image, then extracting the texture features of the
-	detected tumor using Gray Level Co- occurrence Matrix (GLCM) and then
-	classified using neuro-fuzzy classifier. Amin and Mageed \cite{bac3}
-	proposed neural network and segmentation base system to automatically detect
-	the tumor in brain MRI images. The Principal Component Analysis (PCA) is
-	used for feature extraction and then Multi-Layer Perceptron (MLP) is used
-	classify the extracted features of MRI brain image.  The average recognition
-	rate is 88.2\% and peak recognition rate is 96.7\%.  Sapra \cite{bac4}
-	proposed image segmentation technique to detect brain tumor from MRI images
-	and then Probabilistic Neural Network (PNN)  is used for automated brain
-	tumor classification in MRI scans. PNN system proposed handle the process of
-	brain tumor classification more accurately. Suchita and Lalit \cite{bac5}
-	proposed unsupervised neural network learning technique for classification
-	of brain MRI images.  The MRI brain images are first preprocessed which
-	include noise filtering, edge detection, then the tumor is extracted using
-	segmentation. The texture features are extracted using Gray-Level
-	Co-occurrence Matrix(GLCM) and then Self-Organizing Maps (SOM) are used to
-	classify the brain as normal or abnormal brain, that is, whether it contain
-	tumor or not. Rajeshwari and Sharmila \cite{bac6} proposed preprocessing
-	techniques which are used to improve the quality of MRI image before using
-	it into an application. The average, median and wiener filters are used for
-	noise removal and interpolation based Discrete Wavelet Transform (DWT)
-	technique is used for resolution enhancement. The Peak Signal to Noise Ratio
-	(PSNR) is used for evaluation of these techniques.
+	\input{backgournd.tex}
 
@@
 
-	\section{Result}%
+	\section[result]{Result}%
 	\label{sec:result}
@@
 	The evaluated models are plotted on graph for better understanding of data.
+
+	\begin{figure}[H]
+		\centering
+		\subfloat[cnn using tensorflow]
+		{\includegraphics[width=0.4\linewidth]
+		{imgs/tf_cnn.png}\label{tf_cnn_cmp}}
+		\hspace{0.5cm}
+		\subfloat[cnn using fast.ai]
+		{\includegraphics[width=0.5\linewidth]
+		{imgs/fastai_cnn.png}\label{fastai_vgg16_cmp}}
+		\caption{CNN implemented in fast.ai and tensorflow}
+		\label{CNN in fast.ai and tensorflow}
+	\end{figure}
 
@@
 
-	\begin{figure}[ht]
+	\begin{figure}[H]
 		\centering
-		\includegraphics[width=\linewidth]{imgs/result.png}
-		\caption{Predictions made by the VGG16 model in tensorflow on random data}%
-		\label{fig:result}
+		\subfloat[prediction made by VGG16 implemented in tensorflow]
+		{\includegraphics[width=0.5\linewidth]
+		{imgs/result.png}\label{vgg16_tf}}
+		\hspace{0.3cm}
+		\subfloat[prediction made by ResNet50 implemented in fast.ai]
+		{\includegraphics[width=0.5\linewidth]
+		{imgs/result_fast_ai.png}\label{resnet_fastai}}
+		\caption{Comparing Predictions made by models}
+		\label{fig:Results_Comparison}
 	\end{figure}
 
-	As it can be seen from Figure~\ref{fig:result} there are some false
+	As it can be seen from Figure~\ref{fig:Results_Comparison} there are some false
 	positives in our predictions.
+
+	\section[appendix]{Appendix}%
+	\label{sec:Appendix}
+
+	\subsection{Tensorflow Implementation}%
+	\label{sub:Tensorflow Implementation}
+
+	\subsubsection{CNN}
+	\input{tf_cnn.tex}
+
+	\subsubsection{VGG 16}
+	\input{tf_vgg.tex}
+
+	\subsubsection{ResNet 50}
+	\input{tf_reset.tex}
+
+	\subsubsection{Prediction}
+	\input{tf_prediction.tex}
+
+	\subsection{fast.ai Implementation}%
+	\label{sub:fast.ai Implementation}
+
+	\subsubsection{CNN}
+	\input{fastai_cnn.tex}
+
+	\textbf{Prediction}
+	\input{fastai_cnn_pred.tex}
+
+	\subsubsection{VGG 16}
+	\input{fastai_vgg.tex}
+
+	\textbf{Prediction}
+	\input{fastai_vgg_pred.tex}
+
+	\subsubsection{ResNet 50}
+	\input{fastai_resnet.tex}
+
+	\textbf{Prediction}
+	\input{fastai_resnet_pred.tex}
 

### 2021-07-25 backgournd.tex
predictions for fast ai

	Natarajan \cite{bac1} proposed brain tumor detection method for MRI brain
	images. The MRI brain images are first preprocessed using median filter,
	then segmentation of image is done using threshold segmentation and
	morphological operations are applied and then finally, the tumor region is
	obtained using image subtraction technique. This approach gives the exact
	shape of tumor in MRI brain image. Joshi \cite{bac2} proposed brain tumor
	detection and classification system in MR images by first extracting the
	tumor portion from brain image, then extracting the texture features of the
	detected tumor using Gray Level Co-occurrence Matrix (GLCM) and then
	classified using neuro-fuzzy classifier. Amin and Mageed \cite{bac3}
	proposed neural network and segmentation base system to automatically detect
	the tumor in brain MRI images. The Principal Component Analysis (PCA) is
	used for feature extraction and then Multi-Layer Perceptron (MLP) is used
	classify the extracted features of MRI brain image. The average recognition
	rate is 88.2\% and peak recognition rate is 96.7\%. Sapra \cite{bac4}
	proposed image segmentation technique to detect brain tumor from MRI images
	and then Probabilistic Neural Network (PNN) is used for automated brain
	tumor classification in MRI scans. PNN system proposed handle the process of
	brain tumor classification more accurately. Suchita and Lalit \cite{bac5}
	proposed unsupervised neural network learning technique for classification
	of brain MRI images. The MRI brain images are first preprocessed which
	include noise filtering, edge detection, then the tumor is extracted using
	segmentation. The texture features are extracted using Gray-Level
	Co-occurrence Matrix(GLCM) and then Self-Organizing Maps (SOM) are used to
	classify the brain as normal or abnormal brain, that is, whether it contain
	tumor or not. Rajeshwari and Sharmila \cite{bac6} proposed preprocessing
	techniques which are used to improve the quality of MRI image before using
	it into an application. The average, median and wiener filters are used for
	noise removal and interpolation based Discrete Wavelet Transform (DWT)
	technique is used for resolution enhancement. The Peak Signal to Noise Ratio
	(PSNR) is used for evaluation of these techniques.

	George and Karnan \cite{George2012MRIBI} proposed MRI image enhancement
	technique based on Histogram Equalization and Center Weighted Median (CWM)
	filter as they are used to enhance the MRI image more effectively. Daljit
	Singh et \cite{Funmilola2015ClassificationOA} proposed a hybrid technique
	for automatic classification of MRI images by first extracting the features
	using Principal Component Analysis (PCA) and Gray-Level Co-occurrence
	Matrix(GLCM) and then extracted features are fed as an input to Support
	Vector Machine(SVM) classifier which classifies the brain image as normal or
	abnormal. Gadpayleand and Mahajani \cite{9074375} proposed brain tumour
	detection and classification system. The tumor is extracted using
	segmentation and then texture features are extracted using GLCM and finally
	the BPNN and KNN classifiers are used to classify the MRI brain image into
	normal or abnormal brain. The accuracy is 70\% using KNN classifier and
	72.5\% by using BPNN classifier. Shasidhar et al. in \cite{article} proposed
	modified Fuzzy C-Means (FCM) algorithm for MR brain tumor detection. The
	texture features are extracted from brain MR image and then modified FCM
	algorithm is used for brain tumor detection. The average speed-ups of as
	much as 80 times a traditional FCM algorithm is obtained using the modified
	FCM algorithm. The modified FCM algorithm is a fast alternative to the
	traditional FCM technique.  Rajesh and Malar \cite{inproceedings} proposed
	brain MR image classification based on Rough set theory and feed-forward
	neural network classifier. The features are extracted from MRI images using
	Rough set theory. The selected features are fed as input to Feed Forward
	Neural Network classifier which differentiate between normal and abnormal
	brain and the accuracy of about 90\% is obtained.

	Ramteke and Monali \cite{article2} proposed automatic classification of
	brain MR images in two classes Normal and Abnormal based on image features
	and automatic abnormality detection. The Statistical texture feature set is
	obtained from normal and abnormal images and then KNN classifier is used for
	classifying image. The KNN obtain 80\% classification rate.  Xuan and Liao
	\cite{4297123} proposed statistical structure analysis based tumor
	segmentation technique. The intensity-based, symmetry-based and texture-
	based features are extracted from MR image. Then, classification technique
	using AdaBoost is used to classify the MR image into normal tissues and
	abnormal images. The average accuracy of about 96.82\% is achieved. Othman
	et al. in \cite{5730335} proposed Probabilistic neural network technique for
	brain tumor classification. Firstly, the features are extracted using the
	principal component analysis (PCA) and the classification is performed using
	Probabilistic Neural Network (PNN).  Ibrahim et al. in \cite{inproceedings2}
	proposed Neural Network technique for the classification of the magnetic
	resonance human brain images. The features are extracted using principal
	Component Analysis (PCA) and then Back- Propagation Neural Network is used
	as a classifier to classify MRI brain images as normal or abnormal. The
	classification accuracy of about 96.33\% is obtained. Jafari and Shafaghi
	\cite{article3} proposed a hybrid approach for brain tumor detection in MR
	images based on Support Vector Machines(SVM). The texture and intensity
	features are used. The accuracy of about 83.22\% is achieved and is more
	robust.

	Thus from extensive literature survey we found that most of the current
	brain tumor detection system uses texture, symmetry and intensity as
	features. Texture features are important property of brain as texture
	perception has a very important aspect in the human visual system of
	recognition and interpretation \cite{article4}. Here, we propose extracting
	texture features like energy, contrast, correlation, Homogenity
	\cite{6524466}. Gray Level Co-occurrence Matrix is used for extraction of
	texture features.

	Further we propose the use of ML algorithms to overcome the drawbacks of
	traditional classifiers. We investigate and compare the performance of two
	machine learning algorithms namely MLP and Naive Bayes in this work. Since
	these ML algorithms are found to perform well in most of the pattern
	classification tasks. Neural networks are useful as they can learn complex
	mappings between input and output. They are capable of solving much more
	complicated classification tasks. However, when certain rules cannot be
	modeled exactly, the concept of probability is used, which is the basis for
	Naive Bayes classification.

### 2021-07-25 fastai_cnn.tex
predictions for fast ai

\begin{minted}{python}
import numpy as np
import pandas as pd
import torch
import keras
import tensorflow as tf
import os
import gc
import pathlib
from keras.models import Sequential
from keras.layers import Conv2D, MaxPooling2D, Flatten, Dense, Dropout, BatchNormalization
from sklearn.metrics import confusion_matrix
from fastai import *
from fastai.vision.all import *
from fastai.tabular.all import *
from fastai.text.all import *
from fastai.vision.data import ImageDataLoaders
from fastai.vision.models import *
import torchvision.models as models
from fastai.callback.schedule import lr_find
from fastai.callback.schedule import *
from matplotlib import pyplot as plt
from fastai.imports import *
from fastai.torch_core import *
from fastai.learner import *
from sklearn.model_selection import train_test_split
from sklearn.preprocessing import OneHotEncoder

print(os.listdir("/content/drive/MyDrive/Colab Notebooks/samples"))
DATA_DIR = "/content/drive/MyDrive/Colab Notebooks/samples/Brain_Tumor"
os.listdir(f'{DATA_DIR}')

data = ImageDataLoaders.from_folder(
    DATA_DIR,
    train=".",
    valid_pct=0.2,
    ds_tfms=aug_transforms(
        mult=1.0,
        do_flip=True,
        flip_vert=True,
        max_warp=0,
        max_rotate=10.0,
        max_zoom=1.1,
        max_lighting=0.2,
        p_affine=0.75,
        mode='bilinear',
        pad_mode='reflection',
        align_corners=True,
        min_scale=1.0),
    item_tfms=Resize(224),
    bs=64,
    val_bs=None,
    num_workers=0,
    batch_tfms=Normalize.from_stats(
        *imagenet_stats))

data.show_batch(nrows=4, figsize=(10, 10))

model = nn.Sequential(
    nn.Sequential(
        nn.Sequential(
            nn.Conv2d(3, 64, kernel_size=(3, 3),
			stride=(1, 1), padding=(1, 1)), nn.ReLU(inplace=True),
            nn.Conv2d(64, 64, kernel_size=(3, 3),
			stride=(1, 1), padding=(1, 1)), nn.ReLU(inplace=True),
            nn.MaxPool2d(2, stride=2),
            nn.Conv2d(64, 128, kernel_size=(3, 3),
			stride=(1, 1), padding=(1, 1)), nn.ReLU(inplace=True),
            nn.Conv2d(128, 128, kernel_size=(3, 3),
			stride=(1, 1), padding=(1, 1)), nn.ReLU(inplace=True),
            nn.MaxPool2d(2, stride=2),
            nn.Conv2d(128, 256, kernel_size=(3, 3),
			stride=(1, 1), padding=(1, 1)), nn.ReLU(inplace=True),
            nn.Conv2d(256, 256, kernel_size=(3, 3),
			stride=(1, 1), padding=(1, 1)), nn.ReLU(inplace=True),
            nn.MaxPool2d(2, stride=2),
            nn.Conv2d(256, 512, kernel_size=(3, 3),
			stride=(1, 1), padding=(1, 1)), nn.ReLU(inplace=True),
            nn.Conv2d(512, 512, kernel_size=(3, 3),
			stride=(1, 1), padding=(1, 1)), nn.ReLU(inplace=True),
            nn.MaxPool2d(2, stride=2),
            nn.AdaptiveAvgPool2d(1),
            nn.AdaptiveMaxPool2d(1)
        )
    ),
    nn.Sequential(
        nn.Flatten(),
        nn.BatchNorm1d(512, eps=1e-05, momentum=0.1, affine=True, track_running_stats=True),
        nn.Dropout(p=0.25, inplace=False),
        nn.Linear(in_features=512, out_features=256, bias=False),
        nn.ReLU(),
        nn.BatchNorm1d(256, eps=1e-05, momentum=0.1, affine=True, track_running_stats=True),
        nn.Dropout(p=0.5, inplace=False),
        nn.Linear(in_features=256, out_features=2, bias=False)
    )
)

learner = Learner(data, model, metrics=[accuracy, error_rate])

learner.summary()

learner.lr_find()

learner.fit_one_cycle(10, lr_max=slice(3.3e-4), cbs=[ShowGraphCallback()])

learner.unfreeze()

learner.lr_find()

learner.fit_one_cycle(8, lr_max=slice(7.59e-5), cbs=[ShowGraphCallback()])

learner.export(
    "/content/drive/MyDrive/Colab Notebooks/pretrained_model/cnn/btc4_final.pkl")

interp = ClassificationInterpretation.from_learner(learner)

interp.plot_confusion_matrix(figsize=(8, 8), dpi=60)
\end{minted}

### 2021-07-25 fastai_cnn_pred.tex
predictions for fast ai

\begin{minted}{python}
import numpy as np
import pandas as pd
import fastbook
from fastbook import *
import os
import gc
import pathlib
import fastai.losses
import fastai.layers
from sklearn.metrics import confusion_matrix
from fastai import *
from fastai.vision import *
from fastai.vision.models import *
import torchvision.models as models

learner = load_learner(
    "/content/drive/MyDrive/Colab Notebooks/pretrained_model/cnn/btc4_final.pkl")

def is_true(x):
    if x[0] == 'yes':
        return "Tumor detected."
    else:
        return "Tumor not detected."

img = PILImage.create(
    f"/content/drive/MyDrive/Colab Notebooks/BrainTumor/no/2 no.jpeg")

x = learner.predict(img)

print("Test Result:", is_true(x), "\nProbability:", x[2])
\end{minted}

### 2021-07-28 fastai_cnn.tex
new fastai implementation

@@
 from fastai.text.all import *
+#from fastai.medical.imaging import *
 from fastai.vision.data import ImageDataLoaders
@@
     ds_tfms=aug_transforms(
-        mult=1.0,
+        mult=2.0,
         do_flip=True,
-        flip_vert=True,
-        max_warp=0,
-        max_rotate=10.0,
-        max_zoom=1.1,
-        max_lighting=0.2,
-        p_affine=0.75,
-        mode='bilinear',
-        pad_mode='reflection',
-        align_corners=True,
-        min_scale=1.0),
+        flip_vert=True),
     item_tfms=Resize(224),
     bs=64,
-    val_bs=None,
-    num_workers=0,
     batch_tfms=Normalize.from_stats(
@@
         nn.Sequential(
-            nn.Conv2d(3, 64, kernel_size=(3, 3),
-			stride=(1, 1), padding=(1, 1)), nn.ReLU(inplace=True),
-            nn.Conv2d(64, 64, kernel_size=(3, 3),
-			stride=(1, 1), padding=(1, 1)), nn.ReLU(inplace=True),
+            nn.Conv2d(3, 64, kernel_size=(3, 3), stride=(1, 1), padding=(1, 1)), nn.ReLU(inplace=True),
+            nn.Conv2d(64, 64, kernel_size=(3, 3), stride=(1, 1), padding=(1, 1)), nn.ReLU(inplace=True),
             nn.MaxPool2d(2, stride=2),
-            nn.Conv2d(64, 128, kernel_size=(3, 3),
-			stride=(1, 1), padding=(1, 1)), nn.ReLU(inplace=True),
-            nn.Conv2d(128, 128, kernel_size=(3, 3),
-			stride=(1, 1), padding=(1, 1)), nn.ReLU(inplace=True),
+            nn.Conv2d(64, 128, kernel_size=(3, 3), stride=(1, 1), padding=(1, 1)), nn.ReLU(inplace=True),
+            nn.Conv2d(128, 128, kernel_size=(3, 3), stride=(1, 1), padding=(1, 1)), nn.ReLU(inplace=True),
             nn.MaxPool2d(2, stride=2),
-            nn.Conv2d(128, 256, kernel_size=(3, 3),
-			stride=(1, 1), padding=(1, 1)), nn.ReLU(inplace=True),
-            nn.Conv2d(256, 256, kernel_size=(3, 3),
-			stride=(1, 1), padding=(1, 1)), nn.ReLU(inplace=True),
+            nn.Conv2d(128, 256, kernel_size=(3, 3), stride=(1, 1), padding=(1, 1)), nn.ReLU(inplace=True),
+            nn.Conv2d(256, 256, kernel_size=(3, 3), stride=(1, 1), padding=(1, 1)), nn.ReLU(inplace=True),
             nn.MaxPool2d(2, stride=2),
-            nn.Conv2d(256, 512, kernel_size=(3, 3),
-			stride=(1, 1), padding=(1, 1)), nn.ReLU(inplace=True),
-            nn.Conv2d(512, 512, kernel_size=(3, 3),
-			stride=(1, 1), padding=(1, 1)), nn.ReLU(inplace=True),
+            nn.Conv2d(256, 512, kernel_size=(3, 3), stride=(1, 1), padding=(1, 1)), nn.ReLU(inplace=True),
+            nn.Conv2d(512, 512, kernel_size=(3, 3), stride=(1, 1), padding=(1, 1)), nn.ReLU(inplace=True),
+            nn.Conv2d(512, 512, kernel_size=(3, 3), stride=(1, 1), padding=(1, 1)), nn.ReLU(inplace=True),
             nn.MaxPool2d(2, stride=2),
-            nn.AdaptiveAvgPool2d(1),
-            nn.AdaptiveMaxPool2d(1)
         )
@@
     nn.Sequential(
+        AdaptiveConcatPool2d(1),
         nn.Flatten(),
+        nn.BatchNorm1d(1024, eps=1e-05, momentum=0.1, affine=True, track_running_stats=True),
+        nn.Dropout(p=0.25, inplace=False),
+        nn.Linear(in_features=1024, out_features=512, bias=False),
+        nn.ReLU(),
         nn.BatchNorm1d(512, eps=1e-05, momentum=0.1, affine=True, track_running_stats=True),
-        nn.Dropout(p=0.25, inplace=False),
-        nn.Linear(in_features=512, out_features=256, bias=False),
-        nn.ReLU(),
-        nn.BatchNorm1d(256, eps=1e-05, momentum=0.1, affine=True, track_running_stats=True),
         nn.Dropout(p=0.5, inplace=False),
-        nn.Linear(in_features=256, out_features=2, bias=False)
+        nn.Linear(in_features=512, out_features=2, bias=False)
     )
@@
 
-learner.fit_one_cycle(10, lr_max=slice(3.3e-4), cbs=[ShowGraphCallback()])
-
-learner.unfreeze()
-
-learner.lr_find()
-
-learner.fit_one_cycle(8, lr_max=slice(7.59e-5), cbs=[ShowGraphCallback()])
+learner.fit_one_cycle(13, lr_max=slice(1e-3), cbs=[ShowGraphCallback()])
 
@@
 
+interp.plot_top_losses(25, figsize=(20, 20))
+
 interp.plot_confusion_matrix(figsize=(8, 8), dpi=60)

### 2021-07-31 acknowledgement.tex
changed first 3 pages as aksed

\section*{\hfill \Huge Acknowledgement \hfill}%
\label{sec:Acknowledgement}

% page border
\AddToShipoutPictureBG*{%
\begin{tikzpicture}[overlay,remember picture]
\draw[line width=1.5pt]
	($ (current page.north west) + (1cm,-1cm) $)
	rectangle
	($ (current page.south east) + (-1cm,2cm) $);
\end{tikzpicture}
}

\vspace{3cm}

\onehalfspacing

I take this opportunity to express profound sense of gratitude and respect to
all those who helped me throughout the duration of this project.

\vspace{1cm}

First and foremost, I would like to thank my supervisor of this project, Prof.
\textbf{Kajari Bhattacharjee}, for her valuable time and guidance. Her
willingness to motivate me has contributed tremendously to my project.

\vspace{1cm}

I would also like to thank Prof. \textbf{Srijeeta Chakrabarti}, Head of
Department of Computer Science, for providing with a good environment and
facilities to work on this project.

\vspace{1cm}
%\vfill

I regret any inadvertent omissions.

%\vspace{3cm}
\vfill

\rule{7cm}{0.4pt}

\textbf{Brahmajit Das} - 183313-21-0044

Semester VI (Honours)

Gurudas College

University of Calcutta

Kolkata - 700 054

\singlespacing

### 2021-07-31 paper.tex
changed first 3 pages as aksed

@@
 \usepackage{wrapfig}
+
+% page border
+\usepackage{tikz}
+\usetikzlibrary{calc}
+\usepackage{eso-pic}
+
+% spacing in certificate
+\usepackage{changepage}
+\usepackage{setspace}
 
@@
 	% Title page
-	\begin{titlepage}
-		\begin{center}
-
-			\vspace*{0.5cm}
-
-			% title
-			\Huge
-			\textbf{Brain Tumor Detection}
-
-			\vspace{0.8cm}
-
-			% logo
-			\includegraphics[width=0.4\linewidth]{imgs/cu_logo.png}
-
-			\vspace{1cm}
-
-			\normalsize
-			Department of Computer Science\\
-			Gurudas College\\
-			Calcutta University\\
-			\today
-
-			% subtitle
-			\vspace{0.5cm}
-			\textit{Detection of tumorous cells using machine learning models}
-
-			\vspace{1cm}
-
-			\normalsize
-			Submitted in partial fulfillment for the requirements for the
-			degree Bachelor of Science (Honors) in Computer Science.
-
-			Academic Year: \textbf{2018-2021}
-
-			\vfill
-			% author
-			\textbf{Authors}:
-
-			$\bullet$ Shoptorshi \space\space
-			$\bullet$ Brahmajit \space\space
-			$\bullet$ Rajarshi \space\space
-			$\bullet$ Bhargav
-
-			% supervisor
-			\vspace{1cm}
-			\rule{5cm}{0.4pt}
-
-			\textbf{Supervisor}: Kajari Bhattacharjeee
-
-		\end{center}
-	\end{titlepage}
+	\input{titlepage.tex}
 
 	% certificate page
-	\section*{\hfill \Huge Certificate \hfill}
-	%\thispagestyle{empty}
+	\input{certificate.tex}
 
-	% roman page numbering
-	\pagenumbering{roman}
-
-	\begin{center}
-		\vspace{1cm}
-
-		% logo
-		\includegraphics[width=0.3\linewidth]{imgs/cu_logo.png}
-
-		\vspace{1cm}
-
-		\Large
-		Department of Computer Science\\
-		Gurudas College\\
-		Calcutta University\\
-	\end{center}
-
-	\vspace{1.8cm}
-	This is to certify that the project entitled "Brain tumor detection using
-	Machine Learning models" is a bona fide work of \textbf{Shoptorshi},
-	\textbf{Brahmajit}, \textbf{Rajarshi} and \textbf{Bhargav} submitted to
-	Gurudas College, University of Calcutta; in partial fulfillment of the
-	requirement for the award of the degree "Bachelor of Science (Honors)" in
-	Computer Science.
-	\vfill
-
-	\begin{multicols}{2}
-
-		Supervisor:
-
-		\rule{5cm}{0.4pt}
-
-		\textbf{Kajari Bhattacharjeee}
-
-		\vspace{1cm}
-
-		Department
-
-		Head:
-
-		\rule{5cm}{0.4pt}
-
-		\textbf{Srijeeta Charkraborty}
-
-		\columnbreak
-
-		Principal:
-
-		\rule{5cm}{0.4pt}
-
-		\textbf{Dr. Mausumi Chatterjee}
-
-	\end{multicols}
-
-	\section*{Acknowledgement}
-	\label{sec:Acknowledgement}
-
-	\vspace{1cm}
-
-	I would like to express my special thanks of gratitude to our supervisor
-	\textbf{Kajari Bhattacharjeee}, teachers of our department \textbf{Sonali
-	Gupta} and \textbf{Srijeeta Charkraborty} ( current department head ); as
-	well as our principal ma'am \textbf{Dr. Mausumi Chatterjee} who gave us the
-	golden opportunity to do this wonderful project on \textit{Brain tumor
-	detection}, which has also helped us in doing a lot of research and we came
-	to know about many new things.
-
-	We are really thankful to them.
-
-	\vspace{1cm}
-
-	Secondly we would like to thank the incredible authors of the research
-	papers in our references/citations for providing us with the information.
+	% acknowledgement
+	\input{acknowledgement.tex}
 

### 2021-07-31 paper.tex
changed document type to report and most sections to chapters

@@
-\documentclass[11pt]{article}
+\documentclass[11pt]{report}
 
-% fonts
-\usepackage[T1]{fontenc}
-\usepackage[utf8]{inputenc}
-\usepackage[english]{babel}
-\usepackage{microtype}
-\usepackage{tgschola}
-\usepackage{inconsolata}
-\usepackage{amsmath}
-
-% images
-\usepackage{graphicx}
-\usepackage{subfig}
-\usepackage{float}
-\usepackage{multicol}
-\usepackage[ddmmyyyy]{datetime}
-\usepackage[a4paper, margin=2cm]{geometry}
-\usepackage{wrapfig}
-
-% page border
-\usepackage{tikz}
-\usetikzlibrary{calc}
-\usepackage{eso-pic}
-
-% spacing in certificate
-\usepackage{changepage}
-\usepackage{setspace}
-
-% code listing
-\usepackage{minted}
-\usemintedstyle{tango}
-
-% sections on new page
-\usepackage{titlesec}
-\newcommand{\sectionbreak}{\clearpage}
-%\setcounter{secnumdepth}{0}
-
-% index and clickable toc
-\usepackage{hyperref}
-\hypersetup{
-	colorlinks,
-	citecolor=black,
-	filecolor=black,
-	linkcolor=black,
-	urlcolor=black
-}
-
-% bibliography
-\usepackage{bookmark}
-\usepackage{url}
-\usepackage[
-	backend=biber,
-	style=numeric,
-	%citestyle=ieee
-]{biblatex}
-\usepackage{csquotes}
-
-\addbibresource{bibliography.bib}
-
-% table of content name
-%\usepackage[nottoc]{tocbibind}
-%\renewcommand{\theHsection}{\thepart.section.\thesection}
-%\addto\captionsenglish{% Replace "english" with the language you use
-	%\renewcommand{\contentsname}%
-	%{\hfill \Huge Table of Content \hfill}%
-%}
+\input{imports.tex}
 
@@
 	% abstract
-	\section[abstract]{Abstract}
+	%\section[abstract]{Abstract}
+	\chapter{Abstract}
 
@@
 	\thispagestyle{plain}
-	\begin{center}
-		\Large
-		\textbf{Brain Tumor Detection}
-
-		\vspace{0.4cm}
-		\large
-		Using various machine learning models to detect brain tumor.
-	\end{center}
 
@@
 	\begin{enumerate}
-		\item \textbf{ Data collection }
-		\item \textbf{ Pre-processing }
-		\item \textbf{ Average filtering }
-		\item \textbf{ segmentation }
-		\item \textbf{ feature extraction }
-		\item \textbf{CNN (or any other model) via classification and identification. By
+		\item Data collection
+		\item Pre-processing
+		\item Average filtering
+		\item Segmentation
+		\item Feature extraction
+		\item CNN (or any other model) via classification and identification. By
 			utilizing the DM (data mining) techniques, significant relations and
@@
 			(machine learning) and Data mining are being effectively employed
-			for brain tumor detection and prevention at an early stage.}
+			for brain tumor detection and prevention at an early stage.
 	\end{enumerate}
 
-	\section[introduction]{Introduction}
-	\subsection[domain description]{Domain Description}
+	\chapter{Introduction}
+	\section[domain description]{Domain Description}
 
@@
 
-	\subsection[motivation]{Motivation}
+	\section[motivation]{Motivation}
 	The motivation is to develop a software with better segmentation capability
@@
 
-	\subsection[scope of work]{Scope of Work}
-	\subsubsection[deliverables]{Deliverables}
+	\section[scope of work]{Scope of Work}
+	\subsection[deliverables]{Deliverables}
 	\begin{itemize}
@@
 
-	\subsubsection[scope]{Scope}
+	\section[scope]{Scope}
 	\begin{itemize}
@@
 
-	\section[background]{Background}
+	\chapter{Background}
 	\input{backgournd.tex}
 
-	\section[methodology]{Methodology}
+	\chapter{Methodology}
 
@@
 
-	\subsection{Image Acquisition}%
-	\label{sub:Image Acquisition}
+	\section{Image Acquisition}%
 
@@
 
-	\subsection{Preprocessing}%
-	\label{sub:Preprocessing}
+	\section{Preprocessing}%
 
@@
 
-	\begin{figure}[H]
+	\begin{figure}[ht]
 		\centering
@@
 
-	\subsection{Feature Extraction}%
-	\label{sub:Feature Extraction}
+	\section{Feature Extraction}%
 
@@
 
-	\subsection{Classification}%
-	\label{sub:Classification}
+	\section{Classification}%
 
@@
 
-	\subsection{Convolutional Neural Network}%
-	\label{sub:Convolutional Neural Network}
+	\section{Convolutional Neural Network}%
 
@@
 
-	\subsection{VGG 16}
+	\section{VGG 16}
 
@@
 
-	\subsubsection{Architecture}
-	\label{sssec:vgg arch}
+	\subsection{Architecture}
+	\label{sec:vgg_arch}
 
@@
 
-	\subsubsection{Configuration}
+	\subsection{Configuration}
 
@@
 	to the nets by their names (A–E).  All configurations follow the generic
-	design presented in Section~\ref{sssec:vgg arch} and differ only in the
+	design presented in Section~\ref{sec:vgg_arch} and differ only in the
 	depth: from 11 weight layers in the network A (8 conv. and 3 FC layers) to
@@
 
-	\begin{figure}[h]
+	\begin{figure}[ht]
 		\centering
@@
 
-	\subsection{ResNet 50}%
-	\label{sub:ResNet 50}
+	\section{ResNet 50}%
 
-	\subsubsection{Residual Learning}
+	\subsection{Residual Learning}
 
@@
 
-	\subsubsection{Network Architecture}
+	\subsection{Network Architecture}
 
@@
 
-	\section[implementation]{Implementation}
+	\chapter{Implementation}
 
-	\subsection{Assumptions and Dependencies}%
-	\label{sub:Assumptions and Dependencies}
+	\section{Assumptions and Dependencies}%
 	It is assumed that the MRI scans are collected and processed before feeding
@@
 
-	\subsection{Implementation Methods}%
-	\label{sub:Implementation Methods}
+	\section{Implementation Methods}%
 	After acquiring the data, the data is classified into two classes (binary
@@
 	After training is complete the models are then evaluated (further discussed
-	in Section~\ref{sec:result} )
+	in Chapter~\ref{chap:Res} )
 
-	\section[result]{Result}%
-	\label{sec:result}
+	\chapter{Result}
+	\label{chap:Res}
 
@@
 
-	\section[appendix]{Appendix}%
-	\label{sec:Appendix}
+	\chapter{Appendix}
 
-	\subsection{Tensorflow Implementation}%
-	\label{sub:Tensorflow Implementation}
+	\section{Tensorflow Implementation}%
 
-	\subsubsection{CNN}
+	\section{CNN}
 	\input{tf_cnn.tex}
 
-	\subsubsection{VGG 16}
+	\section{VGG 16}
 	\input{tf_vgg.tex}
 
-	\subsubsection{ResNet 50}
+	\section{ResNet 50}
 	\input{tf_reset.tex}
 
-	\subsubsection{Prediction}
+	\section{Prediction}
 	\input{tf_prediction.tex}
 
-	\subsection{fast.ai Implementation}%
-	\label{sub:fast.ai Implementation}
+	\section{fast.ai Implementation}%
 
-	\subsubsection{CNN}
+	\section{CNN}
 	\input{fastai_cnn.tex}
@@
 
-	\subsubsection{VGG 16}
+	\section{VGG 16}
 	\input{fastai_vgg.tex}
@@
 
-	\subsubsection{ResNet 50}
+	\section{ResNet 50}
 	\input{fastai_resnet.tex}

### 2021-07-31 acknowledgement.tex
text in italic

@@
-\section*{\hfill \Huge Acknowledgement \hfill}%
-\label{sec:Acknowledgement}
+\section*{}%
+
+\begin{center}
+	{
+		\Huge
+		\textbf{Acknowledgement}
+	}
+\end{center}
 
@@
 
+\textit{
 	I take this opportunity to express profound sense of gratitude and respect to
 	all those who helped me throughout the duration of this project.
+}
 
@@
 
+\textit{
 	First and foremost, I would like to thank my supervisor of this project, Prof.
@@
 	willingness to motivate me has contributed tremendously to my project.
+}
 
@@
 
+\textit{
 	I would also like to thank Prof. \textbf{Srijeeta Chakrabarti}, Head of
@@
 	facilities to work on this project.
+}
 
@@
 
+\textit{
 	I regret any inadvertent omissions.
+}
 

### 2021-08-01 paper.tex
made changes to position of images, and more
fixed the border not appearing in acknowledgement page
added a few subsections and subsubsections

@@
-\documentclass[11pt]{report}
+\documentclass[10pt]{report}
 
@@
 
+	\pagenumbering{roman}
 	% Title page
@@
 
-	\subsubsection{Architecture}
+	\subsection{Architecture}
 
@@
 
-	\textbf{Convolutional Layer}:
+	\subsection{Convolutional Layer}:
+
 	In a CNN, the input is a tensor with a shape: (number of inputs) x (input
@@
 
-	\textbf{Pooling Layer}:
+	\subsection{Pooling Layer}:
+
 	Convolutional networks may include local and/or global pooling layers along
@@
 
-	\textbf{ReLU Layer}:
+	\subsection{ReLU Layer}:
 
@@
 
-	\textbf{Fully Connected Layer}
+	\subsection{Fully Connected Layer}
 
@@
 
-	\textbf{Loss Layer}
+	\subsection{Loss Layer}
 
@@
 
-	\textbf{Receptive field}
+	\subsection{Receptive field}
 
@@
 
-	\textbf{Weights}
+	\subsection{Weights}
 
@@
 		\centering
-		\includegraphics[width=\linewidth]{imgs/vgg16_conf}
+		\includegraphics[width=0.5\linewidth]{imgs/vgg16_conf}
 		\caption{VGG16 configuration}%
@@
 	\subsection{Residual Learning}
-
-	\begin{wrapfigure}{r}{0.5\textwidth}
-		\begin{center}
-			\includegraphics[ width=0.5\textwidth ]{imgs/resnet_arch2.png}
-		\end{center}
-		\caption{Resnet Architecture}
-	\end{wrapfigure}
 
@@
 
+	\begin{figure}[H]
+		\centering
+		\includegraphics[width=0.8\linewidth]{imgs/resnet_arch.png}
+		\caption{resnet50 configuration}%
+		\label{fig:resnet conf}
+	\end{figure}
+
 	\subsection{Network Architecture}
+
+	\begin{wrapfigure}{r}{0.5\textwidth}
+		\begin{center}
+			\includegraphics[ width=0.45\textwidth ]{imgs/resnet_arch2.png}
+		\end{center}
+		\caption{Resnet Architecture}
+	\end{wrapfigure}
 
@@
 
-	\textbf{Plain Network}
+	\subsubsection{Plain Network}
 
@@
 
-	\textbf{Residual Network}
+	\subsubsection{Residual Network}
+
 	Based on the above plain network, we insert shortcut connections which turn
@@
 	they are performed with a stride of 2 \cite[4]{he2015deep} .
-
-	\begin{figure}[h]
-		\centering
-		\includegraphics[width=\linewidth]{imgs/resnet_arch.png}
-		\caption{resnet50 configuration}%
-		\label{fig:resnet conf}
-	\end{figure}
 

### 2021-08-02 paper.tex
added small table of content and new chapter (conclution and future work)
corrected background, changed the methodology diagram

@@
 
-	\tableofcontents
+	{\small\tableofcontents}
+	%\tableofcontents
 
@@
 	relies upon \textit{ CNN (Convolution Neural Networks) }, \textit{ VGG 16 }
-	and \textit{ Resent 50 }, determining small 7 x 7 kernels. By incorporating
+	and \textit{ Resnet 50 }, determining small 7 x 7 kernels. By incorporating
 	this single technique, segmentation and classification is accomplished. CNN
@@
 		\centering
-		\includegraphics[width=1\linewidth]{imgs/methodology}
+		\includegraphics[width=0.5\linewidth]{imgs/methodology}
 		\caption{Proposed Methodology}%
@@
 
-	\chapter{Result}
+	\chapter{Experimental Result}
 	\label{chap:Res}
@@
 
+	\chapter{Conclusion and Future Work}
+
 	\chapter{Appendix}

### 2021-08-03 slides.tex
moved to latex from pandoc

\documentclass[10pt, aspectratio=169]{beamer}

\usepackage{tgschola}
\usepackage{subfig}
\usepackage{float}
\usepackage{wrapfig}

\title{Brain Tumor Detection using Machine Learning Models}

\subtitle{B.Sc. Semester VI Project \newline Department of Computer Science, Gurudas College}

\usetheme{Madrid}

\date{}

\author[Rajarshi, Bhargav, Soptorshi, Brahmajit] {
	Bhargav Basu \texorpdfstring{\\} \and
	Soptorshi Bhattacharjee \texorpdfstring{\\} \and
	Brahmajit Das \texorpdfstring{\\} \and
	Rajarshi Sardar
}

\institute[Gurudas College]{Gurudas College, Calcutta University}

\begin{document}

	\frame{\titlepage}

	\begin{frame}
		\frametitle{Overview}
		\tableofcontents
	\end{frame}

	\section{Motivation}
	\begin{frame}
		\frametitle{Motivation}

		The motivation is to develop a software with better segmentation
		capability for use in medical imaging to detect diseases like brain
		tumor. Image segmentation has been identified as the key problem of
		medical image analysis and remains a popular and challenging area of
		research. Image segmentation is increasingly used in many clinical and
		research applications to analyze medical imaging datasets; which
		motivated us to present a snapshot of dynamically changing field of
		medical image segmentation.

		\vspace{0.5cm}

		The motivation of this work is to increase patient safety by providing
		better and more precise data for medical decision.
	\end{frame}

	\section{Domain Description}

	\begin{frame}
		\frametitle{Domain Description}

		\begin{itemize}
			\item
			\textbf{Neurological Examination}: It is a series of test to measures
			the function of the patients nervous system and also his/her physical
			and mental alertness. \pause
			\item
			\textbf{Machine Learning}: Machine learning approaches address these
			problems by mainly using hand-crafted features (or pre-defined
			features). \pause
		   \item
		   \textbf{Brain Scans}: Brain scan is a picture of the internal
		   structure of the brain. A specialized machine takes a scan in the
		   same way as a digital camera takes a photograph.
		\end{itemize}
	\end{frame}

	\section{Background}

	\begin{frame}
		\frametitle{Background}

		We propose the use of ML algorithms to overcome the drawbacks of
		traditional classifiers. We investigate and compare the performance of
		various machine learning models, namely \textbf{CNN}, \textbf{VGG 16}
		and \textbf{ ResNet 50 }; implemented using the frameworks Tensorflow
		and fast.ai.
	\end{frame}

	\section{Methodology}

	\begin{frame}
		\frametitle{Methodology}

		\vspace{-2.5cm}

		\begin{figure}[h]
			\centering
			\includegraphics[width=\linewidth]{imgs/flowchart}
			\caption{Proposed Methodology}%
			\label{fig:prop_methodology}
		\end{figure}

	\end{frame}

	\subsection{Image Acquisition}

	\begin{frame}
		\frametitle{Methodology}
		\framesubtitle{Image Acquisition}
		The MRI brain images are acquired and are given as input to
		pre-processing stage.

		\begin{figure}[H]
			\centering
			\subfloat[MRI scan shown no presence of tumor]
			{\includegraphics[width=0.25\textwidth]
			{imgs/pred1.jpg}\label{scan2}}
			\hspace{0.2cm}
			\subfloat[MRI scan of a tumorous cell]
			{\includegraphics[width=0.2\textwidth]
			{imgs/Y100.JPG}\label{scan1}}
			\caption{MRI Scans}
			\label{MRIScans}
		\end{figure}
	\end{frame}

	\subsection{Preprocessing}

	\begin{frame}
		\frametitle{Methodology}
		\frametitle{Preprocessing}

		Preprocessing is needed as it provides improvement in image data which
		enhances some of the image features which are important for further
		processing.

		\vspace{1cm}

		Preprocessing includes:

		\begin{itemize}
			\item Binarization
			\item Filtering
			\item Edge Detection
			\item Segmentation
		\end{itemize}
	\end{frame}

	\begin{frame}
		\begin{figure}[ht]
			\centering
			\subfloat[Original Image]
			{\includegraphics[width=0.2\linewidth]
			{imgs/Y100.JPG}\label{original}}
			\hspace{0.5cm}
			\subfloat[Filtered Imaage]
			{\includegraphics[width=0.2\linewidth]
			{imgs/median_filtering.png}\label{smooted image}}
			\hspace{0.5cm}
			\subfloat[Edge Detection]
			{\includegraphics[width=0.2\linewidth]
			{imgs/edges_detection.png}\label{edge detection}}
			\hspace{0.5cm}
			\subfloat[Segmentation]
			{\includegraphics[width=0.2\linewidth]
			{imgs/segmentation.png}\label{segmentation}}
			\caption{preprocessing operations}
			\label{Preprocessing Operations}
		\end{figure}
	\end{frame}
\end{document}

### 2021-08-03 backgournd.tex

@@
 	Further we propose the use of ML algorithms to overcome the drawbacks of
-	traditional classifiers. We investigate and compare the performance of two
-	machine learning algorithms namely MLP and Naive Bayes in this work. Since
-	these ML algorithms are found to perform well in most of the pattern
+	traditional classifiers. We investigate and compare the performance of three
+	machine learning models namely CNN, VGG-16 and Resnet-50 in this work. Since
+	these ML models are found to perform well in most of the pattern
 	classification tasks. Neural networks are useful as they can learn complex
 	mappings between input and output. They are capable of solving much more
-	complicated classification tasks. However, when certain rules cannot be
-	modeled exactly, the concept of probability is used, which is the basis for
-	Naive Bayes classification.
+	complicated classification tasks.

### 2021-08-03 fastai_cnn.tex

@@
 from fastai.text.all import *
-#from fastai.medical.imaging import *
 from fastai.vision.data import ImageDataLoaders
@@
         nn.Sequential(
-            nn.Conv2d(3, 64, kernel_size=(3, 3), stride=(1, 1), padding=(1, 1)), nn.ReLU(inplace=True),
-            nn.Conv2d(64, 64, kernel_size=(3, 3), stride=(1, 1), padding=(1, 1)), nn.ReLU(inplace=True),
+            nn.Conv2d(3, 64, kernel_size=(3, 3),
+			stride=(1, 1), padding=(1, 1)), nn.ReLU(inplace=True),
+            nn.Conv2d(64, 64, kernel_size=(3, 3),
+			stride=(1, 1), padding=(1, 1)), nn.ReLU(inplace=True),
             nn.MaxPool2d(2, stride=2),
-            nn.Conv2d(64, 128, kernel_size=(3, 3), stride=(1, 1), padding=(1, 1)), nn.ReLU(inplace=True),
-            nn.Conv2d(128, 128, kernel_size=(3, 3), stride=(1, 1), padding=(1, 1)), nn.ReLU(inplace=True),
+            nn.Conv2d(64, 128, kernel_size=(3, 3),
+			stride=(1, 1), padding=(1, 1)), nn.ReLU(inplace=True),
+            nn.Conv2d(128, 128, kernel_size=(3, 3),
+			stride=(1, 1), padding=(1, 1)), nn.ReLU(inplace=True),
             nn.MaxPool2d(2, stride=2),
-            nn.Conv2d(128, 256, kernel_size=(3, 3), stride=(1, 1), padding=(1, 1)), nn.ReLU(inplace=True),
-            nn.Conv2d(256, 256, kernel_size=(3, 3), stride=(1, 1), padding=(1, 1)), nn.ReLU(inplace=True),
+            nn.Conv2d(128, 256, kernel_size=(3, 3),
+			stride=(1, 1), padding=(1, 1)), nn.ReLU(inplace=True),
+            nn.Conv2d(256, 256, kernel_size=(3, 3),
+			stride=(1, 1), padding=(1, 1)), nn.ReLU(inplace=True),
             nn.MaxPool2d(2, stride=2),
-            nn.Conv2d(256, 512, kernel_size=(3, 3), stride=(1, 1), padding=(1, 1)), nn.ReLU(inplace=True),
-            nn.Conv2d(512, 512, kernel_size=(3, 3), stride=(1, 1), padding=(1, 1)), nn.ReLU(inplace=True),
-            nn.Conv2d(512, 512, kernel_size=(3, 3), stride=(1, 1), padding=(1, 1)), nn.ReLU(inplace=True),
+            nn.Conv2d(256, 512, kernel_size=(3, 3),
+			stride=(1, 1), padding=(1, 1)), nn.ReLU(inplace=True),
+            nn.Conv2d(512, 512, kernel_size=(3, 3),
+			stride=(1, 1), padding=(1, 1)), nn.ReLU(inplace=True),
+            nn.Conv2d(512, 512, kernel_size=(3, 3),
+			stride=(1, 1), padding=(1, 1)), nn.ReLU(inplace=True),
             nn.MaxPool2d(2, stride=2),
@@
         nn.Flatten(),
-        nn.BatchNorm1d(1024, eps=1e-05, momentum=0.1, affine=True, track_running_stats=True),
+        nn.BatchNorm1d(1024, eps=1e-05, momentum=0.1,
+		affine=True, track_running_stats=True),
         nn.Dropout(p=0.25, inplace=False),
@@
         nn.ReLU(),
-        nn.BatchNorm1d(512, eps=1e-05, momentum=0.1, affine=True, track_running_stats=True),
+        nn.BatchNorm1d(512, eps=1e-05, momentum=0.1,
+		affine=True, track_running_stats=True),
         nn.Dropout(p=0.5, inplace=False),

### 2021-08-03 slides.tex
done till results, need adding result values and graphs

@@
 
-		\vspace{-2.5cm}
-
 		\begin{figure}[h]
 			\centering
-			\includegraphics[width=\linewidth]{imgs/flowchart}
+			\includegraphics[width=0.7\linewidth]{imgs/methodology}
 			\caption{Proposed Methodology}%
@@
 		\frametitle{Methodology}
-		\frametitle{Preprocessing}
+		\framesubtitle{Preprocessing}
 
@@
 	\end{frame}
+
+	\subsection{Feature Extraction}
+
+	\begin{frame}
+		\frametitle{Methodology}
+		\framesubtitle{Feature Extraction}
+
+		When input to an algorithm is very large and redundant to be processed,
+		it is transformed into reduced representative set of features called
+		feature vector.
+
+		\vspace{1cm}
+
+		These features are extracted using Gray Level Co-occurrence Matrix
+		(GLCM) as it is robust method with high performance.
+	\end{frame}
+
+	\subsection{Classification}
+
+	\begin{frame}
+		\frametitle{Methodology}
+		\framesubtitle{Classification}
+
+		The Machine learning algorithms are used for classification of MR brain
+		image either as normal or abnormal.  The major aim of ML algorithms is
+		to automatically learn and make intelligent decisions.
+
+		\vspace{0.5cm}
+
+		For classification we are using \textbf{CNN}, \textbf{VGG 16} and
+		\textbf{ResNet 50}.
+
+		\vspace{0.5cm}
+
+		For this project we are using binary classification, two classes one for
+		normal and another for abnormal.
+
+	\end{frame}
+
+	\section{Deep learning}
+
+	\begin{frame}
+		\frametitle{Deep Learning}
+		\framesubtitle{Why deep learning?}
+
+		\begin{block}{Image Classification}
+			Image classification is where a computer can analyze an image and
+			identify the ‘class’ the image falls under.
+		\end{block}
+
+		\begin{block}{What is deep learning?}
+			Deep learning is a type of machine learning; a subset of artificial
+			intelligence (AI) that allows machines to learn from data. Deep
+			learning involves the use of computer systems known as neural
+			networks.
+		\end{block}
+
+		\begin{block}{Why use deep learning for image classification}
+			Deep learning allows machines to identify and extract features from
+			images. This means they can learn the features to look for in images
+			by analysing lots of pictures. So, programmers don’t need to enter
+			these filters by hand.
+		\end{block}
+
+	\end{frame}
+
+	\section{Models}
+
+	\begin{frame}
+		\frametitle{Model}
+		\framesubtitle{CNN}
+
+		CNN or Convolutional Neural Network a class of artificial neural
+		network, most commonly applied to analyze visual imagery.They are also
+		known as shift invariant or space invariant artificial neural networks
+		(SIANN), based on the shared-weight architecture of the convolution
+		kernels or filters that slide along input features and provide
+		translation equivariant responses known as feature maps.
+
+	\end{frame}
+
+	\begin{frame}
+		\begin{figure}[h]
+			\centering
+			\includegraphics[width=\linewidth]{imgs/cnn_arch.png}
+			\caption{CNN's architecture}%
+			\label{fig:imgs/cnn_arch}
+		\end{figure}
+	\end{frame}
+
+	\begin{frame}
+		\frametitle{Model}
+		\framesubtitle{VGG 16}
+
+		VGG 16 is is a significantly more accurate ConvNet architecture, which
+		not only achieve state-of-the-art accuracy on ILSVRC classification and
+		localisation tasks, but are also applicable to other image recognition
+		datasets, where they achieve excellent performance even when used as a
+		part of a relatively simple pipelines (e.g. deep features classified by
+		a linear SVM without fine-tuning).
+	\end{frame}
+
+	\begin{frame}
+		\begin{figure}[h]
+			\centering
+			\includegraphics[width=0.8\linewidth]{imgs/vgg16_arch.png}
+			\caption{VGG 16's architecture}%
+			\label{fig:imgs/vgg16_arch}
+		\end{figure}
+	\end{frame}
+
+	\begin{frame}
+		\frametitle{Model}
+		\framesubtitle{ResNet 50}
+
+		ResNet50 is a variant of ResNet model which has 48 Convolution layers
+		along with 1 MaxPool and 1 Average Pool layer. It has $3.8 x 10^9$
+		Floating points operations. It is a widely used ResNet model and we have
+		explored ResNet50 architecture in depth.
+	\end{frame}
+
+	\begin{frame}
+		\begin{figure}[h]
+			\centering
+			\includegraphics[width=\linewidth]{imgs/resnet_arch.png}
+			\caption{Reset's architecture}%
+			\label{fig:imgs/resnet_arch2}
+		\end{figure}
+	\end{frame}
+
+	\section{Implementation}
+
+	\begin{frame}
+		\frametitle{Implementation}
+		\framesubtitle{Assumptions}
+
+		It is assumed that the MRI scans are collected and processed before
+		feeding into the module.
+
+		\vspace{1cm}
+
+		The program is dependent on external modules and are expected to be
+		pre-installed on the system. The modules namely include:
+
+		\vspace{1cm}
+
+		\begin{itemize}
+			\item Tensorflow
+			\item fast.ai
+			\item OpenCV
+			\item matplotlib
+		\end{itemize}
+	\end{frame}
+
+	\begin{frame}
+		\frametitle{Implementation}
+		\framesubtitle{Implementing}
+
+		\begin{itemize}
+			\item Acquire Data (MRI Scans)
+			\item Dividing the data into two classes while keeping the separate
+				batch for prediction
+			\item Build the models using the aforementioned libraries
+			\item Train the model (feed data into the model)
+			\item Evaluate the trained model on the prediction batch
+		\end{itemize}
+	\end{frame}
+
+	\section{Result}
+
+	\begin{frame}
+		\frametitle{Result}
+		\framesubtitle{Comparing the model accuracies}
+
+		\begin{center}
+			\begin{tabular}{| c | c | c |}
+				\hline
+				Model & Implementation using TensorFlow & Implementation using
+				fast.ai \\
+				\hline
+				CNN & 90.31\% & 92.66\% \\
+				\hline
+			\end{tabular}
+		\end{center}
+	\end{frame}
 \end{document}

### 2021-08-03 slides.tex
slides completed

@@
 
-	\frame{\titlepage}
+	\begin{frame}
+		\titlepage
+	\end{frame}
 
@@
 		\frametitle{Overview}
-		\tableofcontents
+		\begin{columns}[totalwidth=0.9\textwidth]
+			\hspace*{2.5cm}
+			\begin{column}{0.35\textwidth}
+				\tableofcontents[sections={1-4}]
+			\end{column}
+			\begin{column}{0.35\textwidth}
+				\tableofcontents[sections={5-9}]
+			\end{column}
+		\end{columns}
 	\end{frame}
@@
 
+		\vspace{-1cm}
+
 		\begin{figure}[h]
 			\centering
-			\includegraphics[width=0.7\linewidth]{imgs/methodology}
+			\includegraphics[width=\textwidth]{imgs/flowchart}
 			\caption{Proposed Methodology}%
@@
 
-		\vspace{1cm}
+		\vspace{0.5cm}
 
@@
 		\end{itemize}
+
+		\begin{block}{Segmentation}
+			Image segmentation is the process of partitioning a digital image into multiple
+			segments (sets of pixels, also known as image objects). The goal of
+			segmentation is to simplify and/or change the representation of an image into
+			something that is more meaningful and easier to analyze.
+		\end{block}
+
 	\end{frame}
@@
 
+		\begin{table}
 			\begin{center}
@@
 					\hline
+					VGG 15 & 97.38\% & 98.15\% \\
+					\hline
+					ResNet 50 & 97.54\% & 99.00\% \\
+					\hline
 				\end{tabular}
+				\caption{Results in percent of the models implemented}
 			\end{center}
+	\end{table}
+	\end{frame}
+
+	\begin{frame}
+		\frametitle{Results}
+		\framesubtitle{CNN implemented using fast.ai and tensorflow}
+		\begin{figure}[H]
+			\centering
+			\subfloat[cnn using tensorflow]
+			{\includegraphics[width=0.4\linewidth]
+			{imgs/tf_cnn.png}\label{tf_cnn_cmp}}
+			\hspace{0.5cm}
+			\subfloat[cnn using fast.ai]
+			{\includegraphics[width=0.5\linewidth]
+			{imgs/fastai_cnn.png}\label{fastai_vgg16_cmp}}
+			\caption{CNN implemented in fast.ai and tensorflow}
+			\label{CNN in fast.ai and tensorflow}
+		\end{figure}
+	\end{frame}
+
+	\begin{frame}
+		\frametitle{Results}
+		\framesubtitle{VGG 16 implemented using fast.ai and tensorflow}
+		\begin{figure}[H]
+			\centering
+			\subfloat[vgg16 using tensorflow]
+			{\includegraphics[width=0.4\linewidth]
+			{imgs/tf_vgg16.png}\label{tf_vgg16}}
+			\hspace{0.5cm}
+			\subfloat[vgg16 using fast.ai]
+			{\includegraphics[width=0.5\linewidth]
+			{imgs/fastai_vgg16.png}\label{fastai_vgg16}}
+			\caption{VGG16 implemented in fast.ai and tensorflow}
+			\label{VGG16 in fast.ai and tensorflow}
+		\end{figure}
+	\end{frame}
+
+	\begin{frame}
+		\frametitle{Results}
+		\framesubtitle{ResNet 50 implemented using fast.ai and tensorflow}
+		\begin{figure}[H]
+			\centering
+			\subfloat[resnet50 using tensorflow]
+			{\includegraphics[width=0.4\linewidth]
+			{imgs/tf_resnet.png}\label{tf_resnet}}
+			\hspace{0.5cm}
+			\subfloat[resnet50 using fast.ai]
+			{\includegraphics[width=0.5\linewidth]
+			{imgs/fastai_resnet.png}\label{fastai_resnet}}
+			\caption{Resnet 50 implemented in fast.ai and tensorflow}
+			\label{ResNet 50 in fast.ai and tensorflow}
+		\end{figure}
+	\end{frame}
+
+	\begin{frame}
+		\frametitle{Results}
+		\framesubtitle{Predictions}
+
+		\begin{figure}[H]
+			\centering
+			\subfloat[prediction made by VGG16 implemented in tensorflow]
+			{\includegraphics[width=0.3\linewidth]
+			{imgs/result.png}\label{vgg16_tf}}
+			\hspace{0.3cm}
+			\subfloat[prediction made by ResNet50 implemented in fast.ai]
+			{\includegraphics[width=0.3\linewidth]
+			{imgs/result_fast_ai.png}\label{resnet_fastai}}
+			\caption{Comparing Predictions made by models}
+			\label{fig:Results_Comparison}
+		\end{figure}
+	\end{frame}
+
+	\section{Future Work}
+	\begin{frame}
+		\frametitle{Future Work}
+
+		We further plan on implementing out experiments on other better machine
+		learning model such as \textbf{GAN}
+
+		\vspace{0.5cm}
+
+		A generative adversarial network (GAN) is a class of machine learning
+		frameworks designed by Ian Goodfellow and his colleagues in 2014. Two
+		neural networks contest with each other in a game (in the form of a
+		zero-sum game, where one agent's gain is another agent's loss).
+
+		\vspace{0.5cm}
+
+		We also plan on increasing out dataset for better training results.
+	\end{frame}
+
+	\begin{frame}
+		\centering
+		\textbf{\Huge Thank you}
 	\end{frame}

### 2021-08-04 slides.tex
moved results table at the bottom
correct image and added roll number of authors

@@
 \author[Rajarshi, Bhargav, Soptorshi, Brahmajit] {
-	Bhargav Basu \texorpdfstring{\\} \and
-	Soptorshi Bhattacharjee \texorpdfstring{\\} \and
-	Brahmajit Das \texorpdfstring{\\} \and
-	Rajarshi Sardar
+	Bhargav Basu (183313-21-0045) \texorpdfstring{\\} \and
+	Soptorshi Bhattacharjee (183313-21-0050) \texorpdfstring{\\} \and
+	Brahmajit Das (183313-21-0044) \texorpdfstring{\\} \and
+	Rajarshi Sardar (183313-21-0055)
 }
@@
 		\begin{itemize}
-			\item Binarization
-			\item Filtering
-			\item Edge Detection
-			\item Segmentation
+			\item \textbf{Binarization}: Converting RGB image to Grayscale
+				image.
+			\item \textbf{Filtering}: Convolving the image using low-pass filter
+				kernel to remove noise.
+			\item \textbf{Edge Detection}: Identifying points in digital image
+				at which the brightness changes sharply.
+			\item \textbf{Segmentation}: Process of partitioning the digital
+				image into multiple segments, with the goal of changing the
+				representation of the image into sometimes more meaningful to
+				analyze.
 		\end{itemize}
-
-		\begin{block}{Segmentation}
-			Image segmentation is the process of partitioning a digital image into multiple
-			segments (sets of pixels, also known as image objects). The goal of
-			segmentation is to simplify and/or change the representation of an image into
-			something that is more meaningful and easier to analyze.
-		\end{block}
 
@@
 	\begin{frame}
-		\frametitle{Result}
-		\framesubtitle{Comparing the model accuracies}
-
-		\begin{table}
-			\begin{center}
-				\begin{tabular}{| c | c | c |}
-					\hline
-					Model & Implementation using TensorFlow & Implementation using
-					fast.ai \\
-					\hline
-					CNN & 90.31\% & 92.66\% \\
-					\hline
-					VGG 15 & 97.38\% & 98.15\% \\
-					\hline
-					ResNet 50 & 97.54\% & 99.00\% \\
-					\hline
-				\end{tabular}
-				\caption{Results in percent of the models implemented}
-			\end{center}
-	\end{table}
-	\end{frame}
-
-	\begin{frame}
 		\frametitle{Results}
@@
 
+	\begin{frame}
+		\frametitle{Result}
+		\framesubtitle{Comparing the model accuracies}
+
+		\begin{table}
+			\begin{center}
+				\begin{tabular}{| c | c | c |}
+					\hline
+					Model & Implementation using TensorFlow & Implementation using
+					fast.ai \\
+					\hline
+					CNN & 90.31\% & 92.66\% \\
+					\hline
+					VGG 15 & 97.38\% & 98.15\% \\
+					\hline
+					ResNet 50 & 97.54\% & 99.00\% \\
+					\hline
+				\end{tabular}
+				\caption{Results in percent of the models implemented}
+			\end{center}
+	\end{table}
+	\end{frame}
+
 	\section{Future Work}

### 2021-08-04 slides.tex
added project guide

@@
 	Brahmajit Das (183313-21-0044) \texorpdfstring{\\} \and
-	Rajarshi Sardar (183313-21-0055)
+	Rajarshi Sardar (183313-21-0055 \texorpdfstring{\\ \vspace{1cm}}) \and
+	Project Guide: Prof. \textbf{Kajari Bhattacharjee}
 }

### 2021-08-04 slides.tex
added acknowledgement

--- 2021-08-04 slides.tex
@@
 	Brahmajit Das (183313-21-0044) \texorpdfstring{\\} \and
-	Rajarshi Sardar (183313-21-0055)
+	Rajarshi Sardar (183313-21-0055) \texorpdfstring{\\ \vspace{1cm}} \and
+	Project Guide: Prof. \textbf{Kajari Bhattacharjee}
 }
@@
 			\begin{column}{0.35\textwidth}
-				\tableofcontents[sections={1-4}]
+				\tableofcontents[sections={1-5}]
 			\end{column}
 			\begin{column}{0.35\textwidth}
-				\tableofcontents[sections={5-9}]
+				\tableofcontents[sections={6-10}]
 			\end{column}
@@
 
+	\section{Acknowledgement}
+
+	\begin{frame}
+		\frametitle{Acknowledgement}
+
+		We take this opportunity to express profound sense of gratitude and respect to
+		all those who helped us throughout the duration of this project.
+
+		\vspace{1cm}
+
+		First and foremost, We would like to thank my supervisor of this project, Prof.
+		\textbf{Kajari Bhattacharjee}, for her valuable time and guidance. Her
+		willingness to motivate me has contributed tremendously to my project.
+
+		\vspace{1cm}
+
+		We would also like to thank Prof. \textbf{Srijeeta Chakrabarti}, Head of
+		Department of Computer Science, for providing with a good environment and
+		facilities to work on this project.
+	\end{frame}
+
 	\begin{frame}

### 2021-08-04 paper.tex
conclusion

@@
 	With the improved technology, not only does the size and resolution of the
-	images grow but also the number of dimensions increases. In the future, we
-	would like to have algorithms which can automatically detect diseases,
-	lesions and tumors, and highlight their locations in the large pile of
-	images.
+	images grow but also the number of dimensions increases.
 
@@
 
+	From this experiment/project we can clearly conclude that the ResNet 50
+	outperforms other machine learning models.
+
+	In the future, I would like to have algorithms which can automatically
+	detect diseases, lesions and tumors, and highlight their locations in the
+	large pile of images.
+
+	I would also like to train using better machine learning models like GAN.
+	A generative adversarial network is a class of machine learning frameworks
+	designed by Ian Goodfellow and his colleagues in 2014. Two neural networks
+	contest with each other in a game. Given a training set, this technique learns
+	to generate new data with the same statistics as the training set.
+
+	I also plan on improving and expanding the dataset, which will greatly
+	increase our experimental results.
+
 	\chapter{Appendix}

### 2021-08-04 slides.tex
grammar and spelling mistakes

@@
 			\hspace{0.5cm}
-			\subfloat[Filtered Imaage]
+			\subfloat[Filtered Image]
 			{\includegraphics[width=0.2\linewidth]
@@
 
-		First and foremost, We would like to thank my supervisor of this project, Prof.
+		First and foremost, We would like to thank our supervisor of this project, Prof.
 		\textbf{Kajari Bhattacharjee}, for her valuable time and guidance. Her
-		willingness to motivate me has contributed tremendously to my project.
+		willingness to motivate us has contributed tremendously to this project.
 
